### 2024-02-13 outputs/paper.Rmd
1

---
  title: "Explaining Hate Crime and Immigrant Conflict: A New Perspective Study of Mate Competition"
subtitle: "Reproduction of 'Hate Crimes and Gender Imbalances: Fears over MateCompetition and Violence against Refugees'(Dancygier, Egami, Jamal & Rischke, 2022)"
author: Guoguo Lv, Xiyou Wang, Yetao Guo
thanks: "Code and data are available at: https://github.com/wxywxy666/Hate-Crimes-and-Gender-Imbalances. A replication of various aspects in this paper are available at: https://doi.org/10.1111/ajps.1259"
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: ""
output:
  bookdown::pdf_document2
toc: TRUE
bibliography: references.bib
---

```{r setup, include=FALSE}
# Load libraries
library(ggplot2)
```

# Introduction

<!-- Background / Broader Context -->

Hate crime and gender imbalance have emerged as a pressing issue in today's society, sparking fears over the disruption of stable relationship formation and social cohesion(FBI 5; Sage books). Explained as the criminal act motivated by bias or prejudice towards particular groups such as race, religion, gender, or identity-based characteristics, hate crimes pose a crucial threat to individuals' and communities' safety. Characterized by disparities in gender imbalance in the portion of men to women within a population has garnered attention for social dynamics and interpersonal relationships due to potential implications (Baoping 7)

The link between hate crime and gender imbalance, with factors interrelated influencing both phenomena, is multifaceted and complex (Chakraborti and Garland 24). Certain groups, especially women and members of marginalized communities, often experience gender-based inequalities and are affected disproportionately by discrimination and acts of violence. Further, whether in the form of skewed sex ratios or imbalance in social opportunities and economic gender imbalances, it can lead to frustrations and resentment feelings among individuals, potentially increasing animosity toward specific groups and increasing hate-motivated likelihood (Carvallo et al.,2023).

Despite increased recognition of hate crime and gender imbalance intertwined nature, comprehensive analysis by assessing their intersection remains limited(James et al.,2021). The current has focused on the aspects isolated from their phenomena, overlooking the intricate interplay between them. Therefore, there is a significant need for studies that explore the the relationship between gender imbalance and hate crimes, thus focusing on the mechanism underlying individual well-being and social cohesion implications.

This study aims to cross the gap by investigating and addressing the following questions:

-   What is the relationship between the proportion of excess males in a municipality and the perceived competition for mates among the population?
-   What is the attitudes towards hate crimes against refugees?
-   What is the relationship between mate competition and support for hate crimes against refugees?

Drawing data from different sources, we seek to elucidate complex phenomena between interconnections and their broader societal implications (FBI 5; Sage books). Through empirical and theoretical analysis rigorously, contribute to a better understanding of these factors during hate-motivated behavior and gender imbalances informing evidence-based intervention and initiatives policies seeking to foster more excellent inclusive gender balance and tolerance in society (Chakraborti and Garland 24).

# Data

## Data Source and Methodology

The data on birth rates per 1,000 women ages 15-44 across all races and demographic population subgroups are obtained from the National Vital Statistics Reports for the years 2015, 2019 and 2020 [@2015birth; @2019birth; @2020birth], which they collected from birth certificates registered in all US states and the District of Colombia. Aggregated data on the number of births for 6 different 5-year cohorts of mothers by their age and birth year is provided by @og, calculated using public birth microdata across the period 1980-1989 from the NBER Natality Database and NCHS microdata from the period 1990-2019 [@nchsR; @nber]. The birth cohorts span the years 1968-1997. The NCHS microdata is restricted use and requires an application to be obtained. We simply used the data that was supplied in the replication packageby @og.

Single-age population counts, among all races from 1969-2019 and by race and Hispanic origin from 1990-2019, is obtained from the CDC SEER database [@nci].

## Attributes

The birth data consists of variables for the year, and birth rates for each population subgroup. For example, for race there are 3 variables: birth rate for whites, birth rate for blacks and birth rate for hispanics. There is birth rate data for 4 population subgroups - age (5-year groupings), race and ethnicity, marital status and mother's level of education. We show a glimpse of the data with variables for race and marital status in table \@ref(tab:birthdata).

```{r birthdata, echo=FALSE}
# Makes table of Ten rows of the birth rate data for years 1980-2020
birth_data %>%
  select(year, brate_all, brate_whitenh, brate_blacknh, brate_hisp, brate_unmarried, brate_married) %>%
  filter(year > 1989) %>%
  slice(1:10) %>%
  kable(
    caption = "Ten rows of the birth rate data for years 1980-2020",
    col.names = c("Year", "All races", "White, non-Hispanic", "Black, non-Hispanic", "Hispanic", "Unmarried", "Married"),
    digits = 1,
    booktabs = TRUE, 
    linesep = ""
  )
```

For the aggregated cohort birth data, the variables are mother's age, birth cohort, number of births and cumulative births. The population data provided by @og gives the population count for women by age, year and state. We group the population count by cohort and mother's age and join this to the cohort birth data, with the first 10 rows of this data shown in table \@ref(tab:birthcohort). We also added a column with the birth years for each cohort for easier interpretation.

```{r, echo=FALSE, warning=FALSE, message=FALSE}
# Process population data to aggregate by cohort
fig5_pop_data1 <- pop_cohort_data %>%
  select(1:32) %>%
  select(-c(stname)) %>%
  group_by(year) %>%
  summarise(across(everything(),sum)) # https://stackoverflow.com/questions/1660124/how-to-sum-a-variable-by-group

fig5_pop_data1 <- fig5_pop_data1 %>%
  pivot_longer(-c(year), names_to = "mage", values_to = "pop")

fig5_pop_data1 <- fig5_pop_data1 %>%
  mutate(mage = as.numeric(str_replace(mage, "fem", ""))) %>%
  mutate(cohort = year - mage) %>%
  mutate(cohort2 = case_when(cohort >= 1968 & cohort <=1972 ~ 1,
                             cohort >= 1973 & cohort <=1977 ~ 2,
                             cohort >= 1978 & cohort <=1982 ~ 3,
                             cohort >= 1983 & cohort <=1987 ~ 4,
                             cohort >= 1988 & cohort <=1992 ~ 5,
                             cohort >= 1993 & cohort <=1997 ~ 6))

fig5_pop_data1 <- na.omit(fig5_pop_data1)
fig5_pop_data1 <- fig5_pop_data1 %>%
  group_by(cohort2, mage) %>%
  summarise(pop = sum(pop))

# Join dataframes for population and birth data
birth_cohort_data <- full_join(birth_cohort_data, fig5_pop_data1, by=c("mage", "cohort2")) %>%
  mutate(cohort_years = case_when(cohort2 == 1 ~ "1968-1972",
                                  cohort2 == 2 ~ "1973-1977",
                                  cohort2 == 3 ~ "1978-1982",
                                  cohort2 == 4 ~ "1983-1987",
                                  cohort2 == 5 ~ "1988-1992",
                                  cohort2 == 6 ~ "1993-1997"))

```

```{r birthcohort, echo=FALSE}
# Make table of First ten rows of the birth cohort data for 6 birth cohorts
birth_cohort_data %>%
  select(2,6,1,3,4,5) %>%
  slice(1:10) %>%
  kable(
    caption = "First ten rows of the birth cohort data for 6 birth cohorts",
    col.names = c("Cohort #", "Birth Years", "Mother's age", "Number of births", "Cumulative births", "Population Count"),
    digits = 1,
    booktabs = TRUE, 
    linesep = ""
  )
```

# Results

## Overall Trend in US Birth Rates

Figure \@ref(fig:fig1) is a replication of Figure 1 in the original paper, and it shows the trend in US birth rates for women ages 15-44. Between 1980 and 2007, the birth rates generally remained between 65-70 births per 1,000 women ages 15-44, with a minimum rate of 63.6 in 1997 and a maximum rate of 70.9 in 1990. The grey dashed lines mark the years of past recessions [@recessions], where we generally see a pattern of decline followed by an uptick in birth rates. After the Great Recession of 2007 however, there was a steady decline, diving below its past minimum rate from 1997 with a birth rate of 63.2 in 2011, and no resurgence so far. The lowest birth rate on the graph occurs in 2020 with 55.8 births per 1,000 women, which is a steep drop of 2.5 from the previous year.

```{r fig1, echo=FALSE, warning=FALSE, message=FALSE, fig.cap="Excess Malesat the Municipality Level and Individuals’Perceived Mate Competition"}
# Load libraries
library(ggplot2)

# Load and clean data for wave 4
d <- readRDS("inputs/data/fig1")
d <- lapply(d, function(x) round(x, 2))

# Classify all p-value
p_values_1st_2nd <- d[[3]][c(1, 4, 7)]
p_values_2nd_3rd <- d[[3]][c(2, 5,8 )]
p_values_total <- d[[3]][c(3, 6, 9)]

# Summary of basic data information
summary_data <- data.frame(
  group = rep(c("All", "Male (18-44)", "Male (30-40)"), each = 3),
  tercile = rep(c("1st tercile", "2nd tercile", "3rd tercile"), 3),
  mean = d[[1]],
  se = d[[2]]
)

# Function to add p-value annotations
add_pvalues <- function(plot, p_values_1st_2nd, p_values_2nd_3rd, p_values_total) {
  plot <- plot + geom_text(data = subset(summary_data, tercile == "2nd tercile" & group == unique(summary_data$group)[1]), 
                           aes(label = sprintf("pv = %.2f", p_values_1st_2nd[1]), y = 0.4),
                           hjust = 1.4, vjust = 30)

  plot <- plot + geom_text(data = subset(summary_data, tercile == "3rd tercile" & group == unique(summary_data$group)[1]), 
                           aes(label = sprintf("pv = %.2f", p_values_2nd_3rd[1]), y = 0.4),
                           hjust = 1.4, vjust = 30)

  plot <- plot + geom_text(data = subset(summary_data, tercile == "2nd tercile" & group == unique(summary_data$group)[1]), 
                           aes(label = sprintf("pv = %.2f", p_values_total[1]), y = 0.4), 
                           vjust = 0, fontface = "italic", size = 5)

  plot <- plot + geom_text(data = subset(summary_data, tercile == "2nd tercile" & group == unique(summary_data$group)[2]), 
                           aes(label = sprintf("pv = %.2f", p_values_1st_2nd[2]), y = 0.5),
                           hjust = 1.4, vjust = 30)

  plot <- plot + geom_text(data = subset(summary_data, tercile == "3rd tercile" & group == unique(summary_data$group)[2]), 
                           aes(label = sprintf("pv = %.2f", p_values_2nd_3rd[2]), y = 0.5),
                           hjust = 1.4, vjust = 30)

  plot <- plot + geom_text(data = subset(summary_data, tercile == "2nd tercile" & group == unique(summary_data$group)[2]), 
                           aes(label = sprintf("pv = %.2f", p_values_total[2]), y = 0.5), 
                           vjust = 0, fontface = "italic", size = 5)

  plot <- plot + geom_text(data = subset(summary_data, tercile == "2nd tercile" & group == unique(summary_data$group)[3]), 
                           aes(label = sprintf("pv = %.2f", p_values_1st_2nd[3]), y = 0.7),
                           hjust = 1.4, vjust = 30)

  plot <- plot + geom_text(data = subset(summary_data, tercile == "3rd tercile" & group == unique(summary_data$group)[3]), 
                           aes(label = sprintf("pv = %.2f", p_values_2nd_3rd[3]), y = 0.7),
                           hjust = 1.4, vjust = 30)

  plot <- plot + geom_text(data = subset(summary_data, tercile == "2nd tercile" & group == unique(summary_data$group)[3]), 
                           aes(label = sprintf("pv = %.2f", p_values_total[3]), y = 0.7), 
                           vjust = 0, fontface = "italic", size = 5)

  return(plot)
}

# Initial plot
p <- ggplot(summary_data, aes(x = tercile, y = mean, group = group)) +
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se), width = 0.2) +
  geom_point() +
  facet_wrap(~group, scales = "free_y") +
  theme_minimal() +
  labs(
    x = "Excess Males",
    y = "Proportion Receiving Male Competition",
    group = "Group Name"
  ) +
  theme(
    strip.text = element_text(size = 20)
  )

# Use function to add p-value annotation
add_pvalues(p, p_values_1st_2nd, p_values_2nd_3rd, p_values_total)
```

## Demographic Factors

Figure \@ref(fig:demgraphs) is a replication of plots A, B, D and E of Figure 2 in the original paper, and shows the trend in birth rates by population subgroups.

```{r demgraphs, echo=FALSE, warning=FALSE, message=FALSE, fig.cap="Proportion of Respondents Who Agree with\nEach of the Four Hate Crime Statements"}
# Load data
points_list <- readRDS("inputs/data/points")
se_p_list <- readRDS("inputs/data/se")

# Bar names
bar_name <- rep("", 5)
bar_name_u <- c("Only Means\n(List)", "Only Means\n(Direct)", "Justified", "Message", "Condemn")

# Set plot format
par(mfrow = c(2, 2), mar = c(5, 5, 4, 2))

# Loop to make 4 panels
for (i in 1:4) {
  point <- points_list[[i]]
  se_p <- se_p_list[[i]]

  base <- barplot(point, ylim = c(0, 0.3), names.arg = bar_name, 
                  col = c("cornflowerblue", rep("lightblue1", 4)),
                  ylab = "Proportion of respondents",
                  las = 2,
                  main = paste("Wave", i))

  arrows(base, point - 1.96*se_p, base, point + 1.96*se_p, 
         lwd = 2, angle = 90, length = 0.05, code = 3,
         col = adjustcolor("black", alpha.f = 0.7))

  mtext(bar_name_u, at = base, side = 1, line = 2.5, cex = 1)
}
```

Plot A shows the trend in birth rates over the period 1980-2020 by five-year age groups. As one would expect, the oldest age group 40-44 has the lowest birth rate. Of note is that the birth rates for older age groups 30-34, 35-39 and 40-44 have been increasing over the period, whereas the younger age groups 15-19, 20-24, 25-29 have been decreasing. The inflection point of increase/decrease is especially noticeable at the year 2007.

Plot B shows the trend in birth rates over the period 1980-2020 for different races and ethnicities. Non-Hispanic black and white groups show a fairly constant trend in birth rates over the period, whereas the Hispanic group shows a significant drop after the Great Recession.

Plot C shows the trend in birth rates over the period 1980-2020 for married vs unmarried mothers. Besides the small increase for unmarried women between 1980 and 1990, the trends do not demonstrate significant change in birth rates. The birth rate is higher for married mothers than unmarried mothers.

Plot D shows the trend in birth rates over the period 1980-2020 for different levels of the mothers' education. The birth rates for highschool graduates, college graduates and mothers with some college education remains in about the same range after 2007. Mothers with no highschool degree have the highest birth rate of the 4 education groups, and the birth rate rises and falls around 2007 before stabilizing to pre-recession levels.

## Cohort effects

To obtain the children ever born, we first calculated the birth rate by dividing the number of births by the population count and then used these values to calculate the cumulative birth rate for each cohort. We then plot the cumulative birth rate against the mother's age, shown in Figure \@ref(fig:cohorttab) which is a replication of Figure 5 of the original paper. The cumulative birth rates for the 3 earlier cohorts are more similar to each other than the 3 later cohorts, with the most recent cohort showing the lowest number of children ever born.

```{r cohorttab, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Estimated Effects of MateCompetition on Support for HateCrime"}
# Calculate points and standard errors again for clarity
point <- readRDS("inputs/data/points")[[5]]
se <- readRDS("inputs/data/se")[[5]]

# Preparation of figure settings
colors <- c("skyblue", "salmon", "lightgreen", "gold", "violet")
pch_values <- c(15, 16, 17, 18, 19)
names_point <- c("Only Means", "Justified", "Message", "Prevent", "Condemn")

par(mar = c(5, 5, 4, 2))

# Initial plot
plot(seq(1:5), point, pch = pch_values, col = colors, ylim = c(-0.05, 0.35), xlim = c(0.5, 5.5), 
     xlab = "", xaxt = "n", ylab = "Estimated Effects", 
     cex.lab = 1.25, cex.axis = 1.25, cex.main = 1.5, cex = 1.5)

segments(seq(1:5), point - 1.96*se, 
         seq(1:5), point + 1.96*se, col = colors, lwd = 2)

Axis(side = 1, at = seq(1:5), labels = names_point, cex.axis = 1.25)

abline(h = 0, lty = 2)

text(2.5, 0.30, "Significant Effects", cex = 0.8)

# Add four arrows
for (i in 1:4) {
  arrows(2.5, 0.29, i, point[i] + 0.02, length = 0.05)
}
```

# Discussion

In Figure \@ref(fig:fig1), we saw that the birth rate enters a persistent decline after the Great Recession in 2007. However, one is left to wonder if this recession is really the event to demarcate this trend in birth rates, since it does not mirror the pattern of recessions prior as we have yet to see any increase in birth rates after the decline.

## Why is the birth rate declining? - Demographic insights

To investigate this idea more, we first turn to the trends among the various demographic subgroups. For the different age groups, the decreasing trend among younger age groups and increasing trend among older age groups points to the idea that women are choosing to have children later in life, an attitudinal change. Only the age 20-24 group seems to show a decrease at the 2007 mark that differs significantly from the years prior. One explanation is that it is the age when most people attend university, and more women are applying for tertiary education and pursuing education before having children. In fact, the National Center for Education Statistics (NCES) data shows a 17.6% increase in undergraduate enrollment among females from 2007 to 2011 [@nces], which coincides perfectly with the 19.1% decrease in birth rates in the 4 years after the Great Recession began in 2007.

For race and ethnicity, the birth rates for Black and White women remains fairly constant and only the Hispanic women show a significant decline in the years 2007-2011 before it plateaus to follow a similar trend to the other two races. @og offer assimilation as a possible explanation with evidence to support this notion from @tavernise and @Parrado2008.

For marital status, married and unmarried women have fairly unchanged birth rates around 2007, so it does not appear to be affected too much by the recession or other events around that time. @og suggests that the small decrease in birth rates for unmarried women is possibly due to the decline in teenage births (ages 15-19) that we saw in Figure \@ref(fig:demgraphs) plot A, since women are marrying later and therefore teenage women make up a larger proportion of the unmarried women population in their childbearing years [@marriage].

For education level, the groups do not appear to demonstrate any change in birth rates with the presence of the Great Recession, except for the no highschool degree group. Its rise and fall in birth rates may be related to the boom in the residential housing market leading up to the recession, where many subprime mortgages were given out, that is, loans to persons with low credit ratings, of which women with a lack of education i.e. no highschool degree would fall under [@insider]. Thus, more women in this group may have chosen to buy homes and start families, and then the recession hit and reversed this effect.

Thus across these demographic groups that we have examined, we note two things: 1) the the declining trend in the total female population of childbearing age is not paralleled equally across its subgroups of age, race and ethnicity, marital status and education level, but 2) specifically we note that younger age groups, Hispanic women and women with no highschool degree showed a significant decrease in birth rates of which only the no highschool degree mamas seem to be related to the Great Recession. We did mention earlier however, that there seems to be an attitudinal change among the women close to the recession - women having children later in life, getting married later, and more women attending colleges and universities - which leads into our discussion of cohort effects.

## Cohort effects - attitudes of a new generation

From Figure \@ref(fig:cohorttab), it was shown that the birth cohorts in years 1968-1982 are quite similar to each other whereas the cohorts born in years 1983-1997 seemed to pull more away with lower birth rates compared to its older counterparts. In fact, these two groupings of years define two distinct generations respectively: Generation X and Generation Y, or the "Millenials" [@gendef]. @millenial conducted a study comparing various lifestyle factors such as education, income, family and housing of Millenials to its prior generations and there are some stark differences.

Notably, women are delaying motherhood as according to a Pew Research Center analysis of population data, 2016 saw 48% of Millennial women having given birth to at least one child at ages 20 to 35 compared to the previous generation where 57% of women were already mothers in 2000 for the same age range [@milmom]. The marriage status for millenials also shows similar figures with 46% of Millennial women ages 25 to 37 being married compared to 57% of Generation X-ers for the same age range, and less millenial women are married for lower levels of education [@millenial]. Additionally, the generations are becoming more racially and ethnically diverse [@postmil] with the population of Hispanics less likely to be foreign-born [@og]. These support our arguments for the change in birth rate trends for women of the different age groups, marital status and race and ethnicity that was discussed in the previous section.

So it now begs the question, why are the attitudes between these two generations so different? We briefly touch on some historical events that surely would have influenced change in Generation Y.

## The Digital Revolution and Third Wave Feminism

The birth years of the millenial generation were characterized by several milestones in the Digital Revolution: the first mobile phone (1984), digital camera (1988) and the World Wide Web (1989) [@stfc]. When the first set of millenials would turn about 10 years old, CERN’s web browser software was released for public use (1991) and commercial dial up internet became available (1992) [@stfc]. In their teenage years to follow, smartphones, social media and high speed internet would be developed creating a tech-savvy generation like never before.

It also happens that Generation X coincides with the years of the second wave of feminism (1963 - 1980s) whereas the formative years of millenials coincide the years of the third wave of feminism [@vox]. The third wave of the feminist movement began with the Anita Hill sexual harassment case in 1991, followed by the "Year of the Woman" in 1992 where a record-breaking number of women candidates were elected to the House of Representatives and Senate (@cawp, as cited in @Dolan1998, p. 272). The third wave of feminism attempts to be distinctive from its predecessor, with some claims in popular literature of it to have a culture of 'girl power', be more open-minded, more racially diverse and inclusive than the second wave, although it is disputed whether some of these claims are exaggerated [@Snyder2008].

Therefore, the influence of technology and mass media that comes with it as well as the different ideologies behind feminism and women empowerment may have shaped the different attitudes we see between the more recent birth cohorts and older cohorts, and these changes may manifest in the decline we see in the birth rates.

## The decline of birth rates - not an effect of the Great Recession?

Back to Figure 1, we noted that the first time the birth rate dipped below minimum from previous years was in 2011, which, upon reflection after our discussion, is almost exactly 20 years after the commercial dial up internet became available and the third wave feminist movement began. 2012 is the year when the birth cohort 1988-1992 was ages 20-24, which is the first cohort to pull away significantly in birth rates to the previous ones. So are these other historical events indirectly responsible for the persistent decline in birth rates by influencing women's attitudes, and not the Great Recession? This is left as food for thought for now, more research would be needed to investigate this question.

# Conclusion

We explored the trend in birth rates in the US for the period 1980-2020 among the total child-bearing population, and demographic subgroups by age, race and ethnicity, marital status and level of education. Overall there is a decline, but the trend oftentimes remains constant for different subgroups and only declines significantly for specific groups such as younger age groups, Hispanic women and women with no highschool degree after 2007. The original paper by @og uses the Great Recession as the event to mark the beginning of the birth rate decline, but although we acknowledge some effect of the recession on decreasing birth rates, we conjecture that the lasting and continuous decline is greater explained by the shifing attitudes towards when and if to have children in the new generation, and that the decline would have been evident even if the recession had not occurred. However, if women are simply choosing to have children later and not to not have children at all, we should expect a pick back up in the birth rates in the coming decade as this group ages.

## Weaknesses and next steps

A weakness is that we only described a subset of the demographic variables that were presented in @og's paper and so the analysis could have been more complete. I do not claim to be an expert on the technlogical revolution or feminism, and we only provided these themes as potential explanatory factors for the change in attitude that is causing the decline in birth rates. More research into how these variables correlate with the different generational groups or birth cohorts is needed to make stronger statistical claims, such as by collecting data on women's beliefs and possibly constructing regression models if appropriate.

\newpage

# References

### 2024-02-14 outputs/paper.rmd
1

--- 2024-02-13 outputs/paper.Rmd
@@
 library(ggplot2)
+library(here)
 ```
@@
 
-Hate crime and gender imbalance have emerged as a pressing issue in today's society, sparking fears over the disruption of stable relationship formation and social cohesion(FBI 5; Sage books).
-Explained as the criminal act motivated by bias or prejudice towards particular groups such as race, religion, gender, or identity-based characteristics, hate crimes pose a crucial threat to individuals' and communities' safety.
-Characterized by disparities in gender imbalance in the portion of men to women within a population has garnered attention for social dynamics and interpersonal relationships due to potential implications (Baoping 7)
+Hate crime and gender imbalance have emerged as a pressing issue in today's society, sparking fears over the disruption of stable relationship formation and social cohesion (FBI 5; Sage books) Explained as the criminal act motivated by bias or prejudice towards particular groups such as race, religion, gender, or identity-based characteristics, hate crimes pose a crucial threat to individuals' and communities' safety.
+Characterized by disparities in gender imbalance in the portion of men to women within a population has garnered attention for social dynamics and interpersonal relationships due to potential implications (shang2022tackling).
 
-The link between hate crime and gender imbalance, with factors interrelated influencing both phenomena, is multifaceted and complex (Chakraborti and Garland 24).
+The link between hate crime and gender imbalance, with factors interrelated influencing both phenomena, is multifaceted and complex (chakraborti2015hate).
 Certain groups, especially women and members of marginalized communities, often experience gender-based inequalities and are affected disproportionately by discrimination and acts of violence.
-Further, whether in the form of skewed sex ratios or imbalance in social opportunities and economic gender imbalances, it can lead to frustrations and resentment feelings among individuals, potentially increasing animosity toward specific groups and increasing hate-motivated likelihood (Carvallo et al.,2023).
+Further, whether in the form of skewed sex ratios or imbalance in social opportunities and economic gender imbalances, it can lead to frustrations and resentment feelings among individuals, potentially increasing animosity toward specific groups and increasing hate-motivated likelihood (leote2023female).
 
-Despite increased recognition of hate crime and gender imbalance intertwined nature, comprehensive analysis by assessing their intersection remains limited(James et al.,2021).
+Although increased recognition of hate crime and gender imbalance intertwined nature, comprehensive analysis by assessing their intersection remains limited(james2021federal).
 The current has focused on the aspects isolated from their phenomena, overlooking the intricate interplay between them.
-Therefore, there is a significant need for studies that explore the the relationship between gender imbalance and hate crimes, thus focusing on the mechanism underlying individual well-being and social cohesion implications.
+Therefore, there is a significant need for studies that explore the relationship between gender imbalance and hate crimes, thus focusing on the mechanism underlying individual well-being and social cohesion implications.
 
@@
 
--   What is the relationship between the proportion of excess males in a municipality and the perceived competition for mates among the population?
--   What is the attitudes towards hate crimes against refugees?
--   What is the relationship between mate competition and support for hate crimes against refugees?
+-   what is the relationship between the proportion of excess males in a municipality and the perceived competition for mates among the population?
+-   what are the attitudes towards hate crimes against refugees?
+-   what is the relationship between mate competition and support for hate crimes against refugees?
 
 Drawing data from different sources, we seek to elucidate complex phenomena between interconnections and their broader societal implications (FBI 5; Sage books).
-Through empirical and theoretical analysis rigorously, contribute to a better understanding of these factors during hate-motivated behavior and gender imbalances informing evidence-based intervention and initiatives policies seeking to foster more excellent inclusive gender balance and tolerance in society (Chakraborti and Garland 24).
+Through empirical and theoretical analysis rigorously, contribute to a better understanding of these factors during hate-motivated behavior and gender imbalances informing evidence-based intervention and initiatives policies seeking to foster more excellent inclusive gender balance and tolerance in society (chakraborti2015hate).
 
@@
 
-The data on birth rates per 1,000 women ages 15-44 across all races and demographic population subgroups are obtained from the National Vital Statistics Reports for the years 2015, 2019 and 2020 [@2015birth; @2019birth; @2020birth], which they collected from birth certificates registered in all US states and the District of Colombia.
-Aggregated data on the number of births for 6 different 5-year cohorts of mothers by their age and birth year is provided by @og, calculated using public birth microdata across the period 1980-1989 from the NBER Natality Database and NCHS microdata from the period 1990-2019 [@nchsR; @nber].
-The birth cohorts span the years 1968-1997.
-The NCHS microdata is restricted use and requires an application to be obtained.
-We simply used the data that was supplied in the replication packageby @og.
-
-Single-age population counts, among all races from 1969-2019 and by race and Hispanic origin from 1990-2019, is obtained from the CDC SEER database [@nci].
-
 ## Attributes
 
-The birth data consists of variables for the year, and birth rates for each population subgroup.
-For example, for race there are 3 variables: birth rate for whites, birth rate for blacks and birth rate for hispanics.
-There is birth rate data for 4 population subgroups - age (5-year groupings), race and ethnicity, marital status and mother's level of education.
-We show a glimpse of the data with variables for race and marital status in table \@ref(tab:birthdata).
-
-```{r birthdata, echo=FALSE}
-# Makes table of Ten rows of the birth rate data for years 1980-2020
-birth_data %>%
-  select(year, brate_all, brate_whitenh, brate_blacknh, brate_hisp, brate_unmarried, brate_married) %>%
-  filter(year > 1989) %>%
-  slice(1:10) %>%
-  kable(
-    caption = "Ten rows of the birth rate data for years 1980-2020",
-    col.names = c("Year", "All races", "White, non-Hispanic", "Black, non-Hispanic", "Hispanic", "Unmarried", "Married"),
-    digits = 1,
-    booktabs = TRUE, 
-    linesep = ""
-  )
-```
-
-For the aggregated cohort birth data, the variables are mother's age, birth cohort, number of births and cumulative births.
-The population data provided by @og gives the population count for women by age, year and state.
-We group the population count by cohort and mother's age and join this to the cohort birth data, with the first 10 rows of this data shown in table \@ref(tab:birthcohort).
-We also added a column with the birth years for each cohort for easier interpretation.
-
-```{r, echo=FALSE, warning=FALSE, message=FALSE}
-# Process population data to aggregate by cohort
-fig5_pop_data1 <- pop_cohort_data %>%
-  select(1:32) %>%
-  select(-c(stname)) %>%
-  group_by(year) %>%
-  summarise(across(everything(),sum)) # https://stackoverflow.com/questions/1660124/how-to-sum-a-variable-by-group
-
-fig5_pop_data1 <- fig5_pop_data1 %>%
-  pivot_longer(-c(year), names_to = "mage", values_to = "pop")
-
-fig5_pop_data1 <- fig5_pop_data1 %>%
-  mutate(mage = as.numeric(str_replace(mage, "fem", ""))) %>%
-  mutate(cohort = year - mage) %>%
-  mutate(cohort2 = case_when(cohort >= 1968 & cohort <=1972 ~ 1,
-                             cohort >= 1973 & cohort <=1977 ~ 2,
-                             cohort >= 1978 & cohort <=1982 ~ 3,
-                             cohort >= 1983 & cohort <=1987 ~ 4,
-                             cohort >= 1988 & cohort <=1992 ~ 5,
-                             cohort >= 1993 & cohort <=1997 ~ 6))
-
-fig5_pop_data1 <- na.omit(fig5_pop_data1)
-fig5_pop_data1 <- fig5_pop_data1 %>%
-  group_by(cohort2, mage) %>%
-  summarise(pop = sum(pop))
-
-# Join dataframes for population and birth data
-birth_cohort_data <- full_join(birth_cohort_data, fig5_pop_data1, by=c("mage", "cohort2")) %>%
-  mutate(cohort_years = case_when(cohort2 == 1 ~ "1968-1972",
-                                  cohort2 == 2 ~ "1973-1977",
-                                  cohort2 == 3 ~ "1978-1982",
-                                  cohort2 == 4 ~ "1983-1987",
-                                  cohort2 == 5 ~ "1988-1992",
-                                  cohort2 == 6 ~ "1993-1997"))
-
-```
-
-```{r birthcohort, echo=FALSE}
-# Make table of First ten rows of the birth cohort data for 6 birth cohorts
-birth_cohort_data %>%
-  select(2,6,1,3,4,5) %>%
-  slice(1:10) %>%
-  kable(
-    caption = "First ten rows of the birth cohort data for 6 birth cohorts",
-    col.names = c("Cohort #", "Birth Years", "Mother's age", "Number of births", "Cumulative births", "Population Count"),
-    digits = 1,
-    booktabs = TRUE, 
-    linesep = ""
-  )
-```
-
 # Results
-
-## Overall Trend in US Birth Rates
-
-Figure \@ref(fig:fig1) is a replication of Figure 1 in the original paper, and it shows the trend in US birth rates for women ages 15-44.
-Between 1980 and 2007, the birth rates generally remained between 65-70 births per 1,000 women ages 15-44, with a minimum rate of 63.6 in 1997 and a maximum rate of 70.9 in 1990.
-The grey dashed lines mark the years of past recessions [@recessions], where we generally see a pattern of decline followed by an uptick in birth rates.
-After the Great Recession of 2007 however, there was a steady decline, diving below its past minimum rate from 1997 with a birth rate of 63.2 in 2011, and no resurgence so far.
-The lowest birth rate on the graph occurs in 2020 with 55.8 births per 1,000 women, which is a steep drop of 2.5 from the previous year.
 
@@
 # Load and clean data for wave 4
-d <- readRDS("inputs/data/fig1")
+d <- readRDS(here::here("inputs/data/fig1"))
 d <- lapply(d, function(x) round(x, 2))
@@
 
-## Demographic Factors
-
-Figure \@ref(fig:demgraphs) is a replication of plots A, B, D and E of Figure 2 in the original paper, and shows the trend in birth rates by population subgroups.
+The chart effectively shows the correlation between the surplus of males in a population and the resultant perceptions of mate competition, which has been divided into three separate cohorts.
+The first cohort comprises the general population, offering a broad perspective on the trend, then more closely in two specific age groups of males: 18-44 and 30-40.
+The data from the chart is organized into terciles, which echoes the changing male surplus levels.
+Using this approach facilitates a better analysis, as it portrays a consistent pattern where the idea of mate competition escalates in relation to the increase in male surplus.
+It is noteworthy to note that this pattern is most marked within the 30-40 age demographic.
+Interpreting this information shows a raised sensitivity to demographic shifts within this group.
+The chart utilizes a clear visual methodology to show these insights.
+The dots represent each perception of the tercile.
+The dots have also been positioned strategically to convey the central tendency of the data.
+P-values with meticulous annotation surround these dots, providing a statistical testament to the importance of the observed trends.
+These p-values serve as a rigorous metric, emphasizing the reliability of the depicted correlations.
 
@@
 # Load data
-points_list <- readRDS("inputs/data/points")
-se_p_list <- readRDS("inputs/data/se")
+points_list <- readRDS(here::here("inputs/data/points"))
+se_p_list <- readRDS(here::here("inputs/data/se"))
 
@@
 
-Plot A shows the trend in birth rates over the period 1980-2020 by five-year age groups.
-As one would expect, the oldest age group 40-44 has the lowest birth rate.
-Of note is that the birth rates for older age groups 30-34, 35-39 and 40-44 have been increasing over the period, whereas the younger age groups 15-19, 20-24, 25-29 have been decreasing.
-The inflection point of increase/decrease is especially noticeable at the year 2007.
-
-Plot B shows the trend in birth rates over the period 1980-2020 for different races and ethnicities.
-Non-Hispanic black and white groups show a fairly constant trend in birth rates over the period, whereas the Hispanic group shows a significant drop after the Great Recession.
-
-Plot C shows the trend in birth rates over the period 1980-2020 for married vs unmarried mothers.
-Besides the small increase for unmarried women between 1980 and 1990, the trends do not demonstrate significant change in birth rates.
-The birth rate is higher for married mothers than unmarried mothers.
-
-Plot D shows the trend in birth rates over the period 1980-2020 for different levels of the mothers' education.
-The birth rates for highschool graduates, college graduates and mothers with some college education remains in about the same range after 2007.
-Mothers with no highschool degree have the highest birth rate of the 4 education groups, and the birth rate rises and falls around 2007 before stabilizing to pre-recession levels.
-
-## Cohort effects
-
-To obtain the children ever born, we first calculated the birth rate by dividing the number of births by the population count and then used these values to calculate the cumulative birth rate for each cohort.
-We then plot the cumulative birth rate against the mother's age, shown in Figure \@ref(fig:cohorttab) which is a replication of Figure 5 of the original paper.
-The cumulative birth rates for the 3 earlier cohorts are more similar to each other than the 3 later cohorts, with the most recent cohort showing the lowest number of children ever born.
+This bar chart contains four panels that present the results of the survey on respondents' level of agreement with four different hate crime statements collected in a total of four waves of the survey study.
+Under the "Estimate from List Experiment," there is only one category titled "Only Means (List)" with a single dark blue bar.
+This bar represents the proportion of respondents who agreed with a statement when asked indirectly, as part of a list experiment.
+The proportion is around 0.15.
+The "Direct Questions" section includes three light blue bars for the categories.
+Each category represents a different hate crime statement where respondents were asked directly.
+"Only Means (Direct)" has a proportion slightly above 0.15, similar to the indirect estimate but with direct questioning.
+"Justified" shows a slightly lower proportion of agreement, just below the 0.15 mark.
+"Message" has a proportion just above 0.15, indicating a similar level of agreement to the "Only Means (Direct)" statement.
+"Condemn" displays the highest agreement, with a proportion close to 0.25, suggesting that more respondents agree with a statement that presumably condemns hate crimes.
+This visual comparison shows differences in respondent agreement levels based on how the questions were asked, with direct questioning generally eliciting higher agreement levels.
 
@@
 # Calculate points and standard errors again for clarity
-point <- readRDS("inputs/data/points")[[5]]
-se <- readRDS("inputs/data/se")[[5]]
+point <- readRDS(here::here("inputs/data/points"))[[5]]
+se <- readRDS(here::here("inputs/data/se"))[[5]]
 
@@
 ```
+This graph depicts the relationship between mate competition and the level of support for hate crime through five distinct categories.
+Each category is represented by a point on the graph, with a vertical line that indicates the confidence interval or error range around the estimate.
+The "Only Means" category has a low estimated effect size around 0.15 with a relatively small confidence interval.
+The "Justified" category shows a slightly higher effect size than "Only Means", also with a small confidence interval.
+The "Message" category has an estimated effect similar to "Justified".
+The "Prevent" category shows the highest estimated effect size than the previous ones, around 0.2.
+Finally, the "Condemn" category has an effect size close to zero, with a confidence interval that crosses the zero line.
+The graph is marked with a horizontal dashed line at the zero mark, which is likely indicating the point of no effect.
+The Significant Effects are marked on the graph above the first four categories, suggesting that these categories' effect size is statistically significant, whereas the remaining category is not explicitly marked as significant.
 
 # Discussion
-
-In Figure \@ref(fig:fig1), we saw that the birth rate enters a persistent decline after the Great Recession in 2007.
-However, one is left to wonder if this recession is really the event to demarcate this trend in birth rates, since it does not mirror the pattern of recessions prior as we have yet to see any increase in birth rates after the decline.
-
-## Why is the birth rate declining? - Demographic insights
-
-To investigate this idea more, we first turn to the trends among the various demographic subgroups.
-For the different age groups, the decreasing trend among younger age groups and increasing trend among older age groups points to the idea that women are choosing to have children later in life, an attitudinal change.
-Only the age 20-24 group seems to show a decrease at the 2007 mark that differs significantly from the years prior.
-One explanation is that it is the age when most people attend university, and more women are applying for tertiary education and pursuing education before having children.
-In fact, the National Center for Education Statistics (NCES) data shows a 17.6% increase in undergraduate enrollment among females from 2007 to 2011 [@nces], which coincides perfectly with the 19.1% decrease in birth rates in the 4 years after the Great Recession began in 2007.
-
-For race and ethnicity, the birth rates for Black and White women remains fairly constant and only the Hispanic women show a significant decline in the years 2007-2011 before it plateaus to follow a similar trend to the other two races.
-@og offer assimilation as a possible explanation with evidence to support this notion from @tavernise and @Parrado2008.
-
-For marital status, married and unmarried women have fairly unchanged birth rates around 2007, so it does not appear to be affected too much by the recession or other events around that time.
-@og suggests that the small decrease in birth rates for unmarried women is possibly due to the decline in teenage births (ages 15-19) that we saw in Figure \@ref(fig:demgraphs) plot A, since women are marrying later and therefore teenage women make up a larger proportion of the unmarried women population in their childbearing years [@marriage].
-
-For education level, the groups do not appear to demonstrate any change in birth rates with the presence of the Great Recession, except for the no highschool degree group.
-Its rise and fall in birth rates may be related to the boom in the residential housing market leading up to the recession, where many subprime mortgages were given out, that is, loans to persons with low credit ratings, of which women with a lack of education i.e.
-no highschool degree would fall under [@insider].
-Thus, more women in this group may have chosen to buy homes and start families, and then the recession hit and reversed this effect.
-
-Thus across these demographic groups that we have examined, we note two things: 1) the the declining trend in the total female population of childbearing age is not paralleled equally across its subgroups of age, race and ethnicity, marital status and education level, but 2) specifically we note that younger age groups, Hispanic women and women with no highschool degree showed a significant decrease in birth rates of which only the no highschool degree mamas seem to be related to the Great Recession.
-We did mention earlier however, that there seems to be an attitudinal change among the women close to the recession - women having children later in life, getting married later, and more women attending colleges and universities - which leads into our discussion of cohort effects.
-
-## Cohort effects - attitudes of a new generation
-
-From Figure \@ref(fig:cohorttab), it was shown that the birth cohorts in years 1968-1982 are quite similar to each other whereas the cohorts born in years 1983-1997 seemed to pull more away with lower birth rates compared to its older counterparts.
-In fact, these two groupings of years define two distinct generations respectively: Generation X and Generation Y, or the "Millenials" [@gendef].
-@millenial conducted a study comparing various lifestyle factors such as education, income, family and housing of Millenials to its prior generations and there are some stark differences.
-
-Notably, women are delaying motherhood as according to a Pew Research Center analysis of population data, 2016 saw 48% of Millennial women having given birth to at least one child at ages 20 to 35 compared to the previous generation where 57% of women were already mothers in 2000 for the same age range [@milmom].
-The marriage status for millenials also shows similar figures with 46% of Millennial women ages 25 to 37 being married compared to 57% of Generation X-ers for the same age range, and less millenial women are married for lower levels of education [@millenial].
-Additionally, the generations are becoming more racially and ethnically diverse [@postmil] with the population of Hispanics less likely to be foreign-born [@og].
-These support our arguments for the change in birth rate trends for women of the different age groups, marital status and race and ethnicity that was discussed in the previous section.
-
-So it now begs the question, why are the attitudes between these two generations so different? We briefly touch on some historical events that surely would have influenced change in Generation Y.
-
-## The Digital Revolution and Third Wave Feminism
-
-The birth years of the millenial generation were characterized by several milestones in the Digital Revolution: the first mobile phone (1984), digital camera (1988) and the World Wide Web (1989) [@stfc].
-When the first set of millenials would turn about 10 years old, CERN’s web browser software was released for public use (1991) and commercial dial up internet became available (1992) [@stfc].
-In their teenage years to follow, smartphones, social media and high speed internet would be developed creating a tech-savvy generation like never before.
-
-It also happens that Generation X coincides with the years of the second wave of feminism (1963 - 1980s) whereas the formative years of millenials coincide the years of the third wave of feminism [@vox].
-The third wave of the feminist movement began with the Anita Hill sexual harassment case in 1991, followed by the "Year of the Woman" in 1992 where a record-breaking number of women candidates were elected to the House of Representatives and Senate (@cawp, as cited in @Dolan1998, p.
-272).
-The third wave of feminism attempts to be distinctive from its predecessor, with some claims in popular literature of it to have a culture of 'girl power', be more open-minded, more racially diverse and inclusive than the second wave, although it is disputed whether some of these claims are exaggerated [@Snyder2008].
-
-Therefore, the influence of technology and mass media that comes with it as well as the different ideologies behind feminism and women empowerment may have shaped the different attitudes we see between the more recent birth cohorts and older cohorts, and these changes may manifest in the decline we see in the birth rates.
-
-## The decline of birth rates - not an effect of the Great Recession?
-
-Back to Figure 1, we noted that the first time the birth rate dipped below minimum from previous years was in 2011, which, upon reflection after our discussion, is almost exactly 20 years after the commercial dial up internet became available and the third wave feminist movement began.
-2012 is the year when the birth cohort 1988-1992 was ages 20-24, which is the first cohort to pull away significantly in birth rates to the previous ones.
-So are these other historical events indirectly responsible for the persistent decline in birth rates by influencing women's attitudes, and not the Great Recession?
-This is left as food for thought for now, more research would be needed to investigate this question.
-
-# Conclusion
-
-We explored the trend in birth rates in the US for the period 1980-2020 among the total child-bearing population, and demographic subgroups by age, race and ethnicity, marital status and level of education.
-Overall there is a decline, but the trend oftentimes remains constant for different subgroups and only declines significantly for specific groups such as younger age groups, Hispanic women and women with no highschool degree after 2007.
-The original paper by @og uses the Great Recession as the event to mark the beginning of the birth rate decline, but although we acknowledge some effect of the recession on decreasing birth rates, we conjecture that the lasting and continuous decline is greater explained by the shifing attitudes towards when and if to have children in the new generation, and that the decline would have been evident even if the recession had not occurred.
-However, if women are simply choosing to have children later and not to not have children at all, we should expect a pick back up in the birth rates in the coming decade as this group ages.
-
-## Weaknesses and next steps
-
-A weakness is that we only described a subset of the demographic variables that were presented in @og's paper and so the analysis could have been more complete.
-I do not claim to be an expert on the technlogical revolution or feminism, and we only provided these themes as potential explanatory factors for the change in attitude that is causing the decline in birth rates.
-More research into how these variables correlate with the different generational groups or birth cohorts is needed to make stronger statistical claims, such as by collecting data on women's beliefs and possibly constructing regression models if appropriate.
 

### 2024-02-14 outputs/paper.Rmd
1

@@
 # Load and clean data for wave 4
-d <- readRDS("inputs/data/fig1")
+d <- readRDS(here::here("inputs/data/fig1data"))
 d <- lapply(d, function(x) round(x, 2))

### 2024-02-14 replications/scripts/data_cleaning.R

@@ -71,7 +71,7 @@ fig1 <- list(mean, se, p_value)
 if (file.exists("inputs/data/fig1")) {
   message("File already exists.")
 } else {
-  saveRDS(fig1, file = "inputs/data/fig1")
+  saveRDS(fig1, file = "inputs/data/fig1data")
 }
 
 ## #################

### 2024-02-14 replications/scripts/fig1_replication.R

@@ -9,7 +9,7 @@
 library(ggplot2)
 
 # Load and clean data for wave 4
-d <- readRDS("inputs/data/fig1")
+d <- readRDS("inputs/data/fig1data")
 d <- lapply(d, function(x) round(x, 2))
 
 # Classify all p-value

### 2024-02-14 outputs/paper.Rmd
1

@@
 thanks: "Code and data are available at: https://github.com/wxywxy666/Hate-Crimes-and-Gender-Imbalances.
-A replication of various aspects in this paper are available at: https://doi.org/10.1111/ajps.1259"
+A replication of various aspects in this paper are available at: https://onlinelibrary.wiley.com/doi/epdf/10.1111/ajps.12595"
 date: "`r format(Sys.time(), '%d %B %Y')`"
-abstract: ""
+abstract: "The study examines the correlation between gender imbalance, specifically the excess of males in a population, and the consequent competition for mates, as well as the attitudes towards hate crimes against refugees.
+Utilizing data from various sources, it aims to illuminate the complex interplay between mate competition and the endorsement of hate crimes, addressing gaps in current research.
+The findings suggest that higher male ratios may contribute to increased mate competition and potentially to greater support for hate-motivated acts against refugees.
+This research underscores the need for policies that promote gender balance and societal tolerance, contributing to the prevention of hate crimes and enhancing social cohesion."
 output:
@@
 ```
-
+\newpage
 # Introduction
@@
 
+The relationship between demographic variables and social attitudes, as depicted in the provided figures, is a complex interplay influenced by many factors. 
+When considering the impact of mate competition on attitudes towards hate crimes (Figure 4), it's crucial to consider the evolutionary psychology perspective, which suggests that competition for mates can increase intergroup hostility and aggression (Buss & Shackelford, 1997).
+These behaviors may be exacerbated in environments with a skewed sex ratio, as individuals may perceive greater competition for potential partners, heightening in-group biases and out-group derogation (Pedersen, 1991).
+In Figure 3, there are two types of responses depicted for the statement "Only Means (List)"—one from the list experiment and one from direct questioning.
+The bar representing the list experiment is indeed lower than that for the direct questioning for the statement "Only Means".
+This could suggest that when individuals are provided with a method that offers anonymity and reduces the pressure to conform to social norms, they might be less likely to agree with statements supporting hate crime, contrary to what might be expected.
+Figure 2 illustrates a positive correlation between the number of excess males in a population and the perception of mate competition, especially among men aged 30-40.
+This demographic trend could imply that in areas with more males, there is an increased sense of rivalry for potential mates.
+While the graph does not directly discuss hate crimes, the concept ties into broader social issues where such demographic imbalances may heighten competitive behaviors, potentially influencing social tensions and actions, including hate crimes.
+To better understand these dynamics, we can look at the intersection of demographic pressures and socio-cultural factors that shape attitudes towards hate crimes.
+Cultural narratives that equate masculinity with dominance and control may influence these attitudes (Connell, 2005).
+In societies where masculinity is closely linked with sexual conquest and competition(Baumeister & Vohs, 2004), excess males may experience heightened psychological stress, potentially contributing to aggressive and hostile behaviors towards out-groups.
+Considering the implications of these findings, it is clear that interventions to reduce support for hate crimes must address not only individual attitudes but also the broader demographic and socio-cultural context.
+This may include public health approaches that focus on changing cultural narratives around masculinity (Courtenay, 2000), as well as social policies aimed at reducing economic and social inequalities that can exacerbate mate competition (Wilkinson & Pickett, 2009).
+
 \newpage

### 2024-02-15 outputs/paper.Rmd
1

--- 2024-02-14 outputs/paper.Rmd
@@
 
+\newpage
+
 # Introduction
 
-<!-- Background / Broader Context -->
+Hate crime and gender imbalance have emerged as a pressing issue in today's society, sparking fears over the disruption of stable relationship formation and social cohesion (FBI 5; Sage books) Explained as the criminal act motivated by bias or prejudice towards particular groups such as race, religion, gender, or identity-based characteristics, hate crimes pose a crucial threat to individuals' and communities' safety.
+Characterized by disparities in gender imbalance in the portion of men to women within a population has garnered attention for social dynamics and interpersonal relationships due to potential implications [@shang2022tackling].
 
-Hate crime and gender imbalance have emerged as a pressing issue in today's society, sparking fears over the disruption of stable relationship formation and social cohesion (FBI 5; Sage books) Explained as the criminal act motivated by bias or prejudice towards particular groups such as race, religion, gender, or identity-based characteristics, hate crimes pose a crucial threat to individuals' and communities' safety.
-Characterized by disparities in gender imbalance in the portion of men to women within a population has garnered attention for social dynamics and interpersonal relationships due to potential implications (shang2022tackling).
+The link between hate crime and gender imbalance, with factors interrelated influencing both phenomena, is multifaceted and complex [@chakraborti2015hate].
+Certain groups, especially women and members of marginalized communities, often experience gender-based inequalities and are affected disproportionately by discrimination and acts of violence.
+Further, whether in the form of skewed sex ratios or imbalance in social opportunities and economic gender imbalances, it can lead to frustrations and resentment feelings among individuals, potentially increasing animosity toward specific groups and increasing hate-motivated likelihood [@leote2023female].
 
-The link between hate crime and gender imbalance, with factors interrelated influencing both phenomena, is multifaceted and complex (chakraborti2015hate).
-Certain groups, especially women and members of marginalized communities, often experience gender-based inequalities and are affected disproportionately by discrimination and acts of violence.
-Further, whether in the form of skewed sex ratios or imbalance in social opportunities and economic gender imbalances, it can lead to frustrations and resentment feelings among individuals, potentially increasing animosity toward specific groups and increasing hate-motivated likelihood (leote2023female).
-
-Although increased recognition of hate crime and gender imbalance intertwined nature, comprehensive analysis by assessing their intersection remains limited(james2021federal).
+Although increased recognition of hate crime and gender imbalance intertwined nature, comprehensive analysis by assessing their intersection remains limited [@james2021federal].
 The current has focused on the aspects isolated from their phenomena, overlooking the intricate interplay between them.
@@
 
--   what is the relationship between the proportion of excess males in a municipality and the perceived competition for mates among the population?
--   what are the attitudes towards hate crimes against refugees?
--   what is the relationship between mate competition and support for hate crimes against refugees?
+-   What is the relationship between the proportion of excess males in a municipality and the perceived competition for mates among the population?
+-   What are the attitudes towards hate crimes against refugees?
+-   What is the relationship between mate competition and support for hate crimes against refugees?
 
 Drawing data from different sources, we seek to elucidate complex phenomena between interconnections and their broader societal implications (FBI 5; Sage books).
-Through empirical and theoretical analysis rigorously, contribute to a better understanding of these factors during hate-motivated behavior and gender imbalances informing evidence-based intervention and initiatives policies seeking to foster more excellent inclusive gender balance and tolerance in society (chakraborti2015hate).
+Through empirical and theoretical analysis rigorously, contribute to a better understanding of these factors during hate-motivated behavior and gender imbalances informing evidence-based intervention and initiatives policies seeking to foster more excellent inclusive gender balance and tolerance in society [@chakraborti2015hate].
 
-# Data
+While the original paper used Stata [@Stata] for data processing and analysis in its replication package, we use R [@R] for all data wrangling and analysis and R packages list [@list] to clean the original data, ggplot2 [@ggplot2] to produce the figures and readstata13 [@readstata13] to read the dta files.
+
+#Data
 
@@
 
+This original data is collected by Rafaela Dancygier, Naoki Egami, Amaney Jamal, and Ramona Rischke, 2022, published in the American Journal of Political Science.
+This article explores the causes of hate crimes against refugees, public and government attitudes towards immigration and ground-breaking analysis of mate competition.
+The study raises two hypotheses: first, whether native men in areas with high competition pressure for male mates will view immigrants as a threat, and second, whether these men will view violence as the only way to get government attention.
+
 ## Attributes
+
+“survey.dta” is a dataset used to produce survey analyzes in the paper (Figure 2, Figure 3, Figure 4), which contains 53 variables and collects a total of 4 waves of survey data.
+Most variables are responses to survey questions.
+For those, we list “Question” and options for “Answer” ranging from Strongly Disagree to Strongly Support, represented by numbers 1-4.
+We only use data directly related to hate crimes.
+For example, in Figure 1, we use the MateComp.cont variable to get the mate competition data (numbers 1-4), and then calculate the p-value to get the results.
 
@@
 
-```{r fig1, echo=FALSE, warning=FALSE, message=FALSE, fig.cap="Excess Malesat the Municipality Level and Individuals’Perceived Mate Competition"}
+```{r fig1, echo=FALSE, warning=FALSE, message=FALSE, fig.cap="Excess Males at the Municipality Level and Individuals’ Perceived Mate Competition"}
 # Load libraries
@@
                            aes(label = sprintf("pv = %.2f", p_values_1st_2nd[1]), y = 0.4),
-                           hjust = 1.4, vjust = 30)
+                           hjust = 1.15, vjust = 25, size = 2.7)
 
@@
                            aes(label = sprintf("pv = %.2f", p_values_2nd_3rd[1]), y = 0.4),
-                           hjust = 1.4, vjust = 30)
+                           hjust = 1.15, vjust = 20, size = 2.7)
 
@@
                            aes(label = sprintf("pv = %.2f", p_values_1st_2nd[2]), y = 0.5),
-                           hjust = 1.4, vjust = 30)
+                           hjust = 1.15, vjust = 25, size = 2.7)
 
@@
                            aes(label = sprintf("pv = %.2f", p_values_2nd_3rd[2]), y = 0.5),
-                           hjust = 1.4, vjust = 30)
+                           hjust = 1.15, vjust = 20, size = 2.7)
 
@@
                            aes(label = sprintf("pv = %.2f", p_values_1st_2nd[3]), y = 0.7),
-                           hjust = 1.4, vjust = 30)
+                           hjust = 1.15, vjust = 25, size = 2.7)
 
@@
                            aes(label = sprintf("pv = %.2f", p_values_2nd_3rd[3]), y = 0.7),
-                           hjust = 1.4, vjust = 30)
+                           hjust = 1.15, vjust = 20, size = 2.7)
 
@@
 
-```{r demgraphs, echo=FALSE, warning=FALSE, message=FALSE, fig.cap="Proportion of Respondents Who Agree with\nEach of the Four Hate Crime Statements"}
+```{r fig2, echo=FALSE, warning=FALSE, message=FALSE, fig.cap="Proportion of Respondents Who Agree with\nEach of the Four Hate Crime Statements"}
 # Load data
@@
 
-  mtext(bar_name_u, at = base, side = 1, line = 2.5, cex = 1)
+  text(base, par("usr")[3] - 0.03, labels = bar_name_u, srt = 45, adj = 1, xpd = TRUE, cex = 1)
 }
@@
 
-```{r cohorttab, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Estimated Effects of MateCompetition on Support for HateCrime"}
+```{r fig3, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Estimated Effects of MateCompetition on Support for HateCrime"}
 # Calculate points and standard errors again for clarity
@@
 
-Axis(side = 1, at = seq(1:5), labels = names_point, cex.axis = 1.25)
+Axis(side = 1, at = seq(1:5), labels = names_point, cex.axis = 1)
 
@@
 ```
+
 This graph depicts the relationship between mate competition and the level of support for hate crime through five distinct categories.
@@
 
+##Finding
+
+Figure \@ref(fig:fig1) illustrates a positive correlation between the number of excess males in a population and the perception of mate competition, especially among men aged 30-40.
+This demographic trend imply that there is an increased sense of rivalry for potential mates in areas with more males.
+While the graph does not directly discuss hate crimes, the concept ties into broader social issues where such demographic imbalances may heighten competitive behaviors, potentially influencing social tensions and actions, including hate crimes.
+In Figure \@ref(fig:fig2), two types of responses are depicted for the statement "Only Means (List)"—one from the list experiment and one from direct questioning.
+The bar representing the list experiment is indeed lower than that for the direct questioning for the statement "Only Means".
+This suggest that when individuals are provided with a method that offers anonymity and reduces the pressure to conform to social norms, they might be less likely to agree with statements supporting hate crime, contrary to what might be expected.
+When considering the impact of mate competition on attitudes towards hate crimes Figure \@ref(fig:fig3), it's crucial to consider the evolutionary psychology perspective, which suggests that competition for mates can increase intergroup hostility and aggression [@Buss1997].
+These behaviors may be exacerbated in environments with a skewed sex ratio, as individuals may perceive greater competition for potential partners, heightening in-group biases and out-group derogation [@Pedersen1991].
+
+##The Interplay of Demographics and Sociocultural Factors
+
+In order to get a better idea of these relationships, what can be examined is the influences of demographic factors and social-cultural attitudes which trigger hate crimes.
+
+##Masculinity
+
+Masculinity, a cultural story where the dominant and controlling is the man, can be the reason for such attitudes [@Connell2005].
+Men are featured in traditional masculinity stories as defenders who are also providers, who are strong physically, violent and who also dominate sexually.
+These cultural stories greatly influence men's perception of their social status and how they perceive that status in their behaviors and actions towards other people.
+Often, in communities where masculinity is equated with sexual conquest and access to women [@Baumeister2004], the superfluous males suffer from psychological stress and anxiety, which might be the cause of aggression and hostility towards other groups.
+This hostility serves as a signal of intergroup conflict, and can be directed at both out-group and in-group members, as part of the competition.
+Similarly, the societal norms of conforming to these masculine ideals can cause greater anxiety and stress among men who feel they do not meet these standards.
+In communities where masculinity is strongly tied to the number of women they are able to conquer, men who are short of potential partners may experience increased psychological stress.
+This stress can be expressed in the form of violence and hostility towards other people.
+Therefore, an increase in the number of hate crimes is a possible outcome.
+
+##Digital media and educational inequality
+
+Furthermore, it is crucial to consider the following elements: digital media, educational inequality, and masculinity among all ages and social classes.
+In the age of digital media, people have their minds conformed to behave in unique ways as no other time has witnessed.
+This is all the more so in the case of social media where assortment of ideas about masculinity and cultural attitudes grows stronger and gets challenged or reinforced there.
+While ruling on one side, the digital trend can give birth to discussions that are more diversified and add new elements to the already established notions.
+They will also be recruitment grounds for crowd them to access and spread extreme ideas as well as hate speech, which in return will just speed up the polarization of public opinion and the violence will come to be the niche of the manhood.
+The digital realm has two different effects on social viewpoints, which could intensify the negative effect of demographic imbalances on the decision-making process of choosing a partner and the subsequent social conflicts.
+
+##Educational inequalities
+
+Educational inequalities, as well, are of great importance when it comes to the development of the public opinion concerning hate crimes.
+In several societies, the socioeconomic status, race, and place of a person are important factors that decide how much education they get that is of high quality.
+However, these differences are the factors that make people perceive the world in different ways and the extent to which they can stand up to the negative stereotypes and prejudices.
+The people who lack a complete education that provides equal opportunities for girls and boys, teach about social justice and the importance of diversity, are more likely to have biased and discriminating views.
+Additionally, it is possible that violent displays of masculinity and intolerance will continue to exist as a consequence of education that either promotes traditional gender standards or minimizes the relevance of critical media literacy.
+
+##Implications
+
+On the implication of the findings, it is evident that programs to eliminate support for hate crimes should include both individual attitude change and the broader context, given that the focus is on demographics and society.
+This covers those promotion of public health that is gender-based and specializes in changing the cultural modeling around masculinity [@Courtenay2000], as well as those reconstructors of social policies envisaging the reduction of economic and social inequalities that can amplify the competition of mates [@Wilkinson2009].
 \newpage

### 2024-02-15 replications/scripts/fig3_replication.R

@@ -24,7 +24,7 @@ plot(seq(1:5), point, pch = pch_values, col = colors, ylim = c(-0.05, 0.35), xli
 segments(seq(1:5), point - 1.96*se, 
          seq(1:5), point + 1.96*se, col = colors, lwd = 2)
 
-Axis(side = 1, at = seq(1:5), labels = names_point, cex.axis = 1.25)
+Axis(side = 1, at = seq(1:5), labels = names_point, cex.axis = 1)
 
 abline(h = 0, lty = 2)
 

### 2024-02-15 paper.Rmd
1

--- 2024-02-15 outputs/paper.Rmd
@@
   bookdown::pdf_document2
+format: pdf
 toc: TRUE
@@
 
-#Data
+# Data
 
@@
 
-# Discussion
-
-##Finding
-
-Figure \@ref(fig:fig1) illustrates a positive correlation between the number of excess males in a population and the perception of mate competition, especially among men aged 30-40.
-This demographic trend imply that there is an increased sense of rivalry for potential mates in areas with more males.
-While the graph does not directly discuss hate crimes, the concept ties into broader social issues where such demographic imbalances may heighten competitive behaviors, potentially influencing social tensions and actions, including hate crimes.
-In Figure \@ref(fig:fig2), two types of responses are depicted for the statement "Only Means (List)"—one from the list experiment and one from direct questioning.
-The bar representing the list experiment is indeed lower than that for the direct questioning for the statement "Only Means".
-This suggest that when individuals are provided with a method that offers anonymity and reduces the pressure to conform to social norms, they might be less likely to agree with statements supporting hate crime, contrary to what might be expected.
-When considering the impact of mate competition on attitudes towards hate crimes Figure \@ref(fig:fig3), it's crucial to consider the evolutionary psychology perspective, which suggests that competition for mates can increase intergroup hostility and aggression [@Buss1997].
-These behaviors may be exacerbated in environments with a skewed sex ratio, as individuals may perceive greater competition for potential partners, heightening in-group biases and out-group derogation [@Pedersen1991].
-
-##The Interplay of Demographics and Sociocultural Factors
-
-In order to get a better idea of these relationships, what can be examined is the influences of demographic factors and social-cultural attitudes which trigger hate crimes.
-
-##Masculinity
-
-Masculinity, a cultural story where the dominant and controlling is the man, can be the reason for such attitudes [@Connell2005].
-Men are featured in traditional masculinity stories as defenders who are also providers, who are strong physically, violent and who also dominate sexually.
-These cultural stories greatly influence men's perception of their social status and how they perceive that status in their behaviors and actions towards other people.
-Often, in communities where masculinity is equated with sexual conquest and access to women [@Baumeister2004], the superfluous males suffer from psychological stress and anxiety, which might be the cause of aggression and hostility towards other groups.
-This hostility serves as a signal of intergroup conflict, and can be directed at both out-group and in-group members, as part of the competition.
-Similarly, the societal norms of conforming to these masculine ideals can cause greater anxiety and stress among men who feel they do not meet these standards.
-In communities where masculinity is strongly tied to the number of women they are able to conquer, men who are short of potential partners may experience increased psychological stress.
-This stress can be expressed in the form of violence and hostility towards other people.
-Therefore, an increase in the number of hate crimes is a possible outcome.
-
-##Digital media and educational inequality
-
-Furthermore, it is crucial to consider the following elements: digital media, educational inequality, and masculinity among all ages and social classes.
-In the age of digital media, people have their minds conformed to behave in unique ways as no other time has witnessed.
-This is all the more so in the case of social media where assortment of ideas about masculinity and cultural attitudes grows stronger and gets challenged or reinforced there.
-While ruling on one side, the digital trend can give birth to discussions that are more diversified and add new elements to the already established notions.
-They will also be recruitment grounds for crowd them to access and spread extreme ideas as well as hate speech, which in return will just speed up the polarization of public opinion and the violence will come to be the niche of the manhood.
-The digital realm has two different effects on social viewpoints, which could intensify the negative effect of demographic imbalances on the decision-making process of choosing a partner and the subsequent social conflicts.
-
-##Educational inequalities
-
-Educational inequalities, as well, are of great importance when it comes to the development of the public opinion concerning hate crimes.
-In several societies, the socioeconomic status, race, and place of a person are important factors that decide how much education they get that is of high quality.
-However, these differences are the factors that make people perceive the world in different ways and the extent to which they can stand up to the negative stereotypes and prejudices.
-The people who lack a complete education that provides equal opportunities for girls and boys, teach about social justice and the importance of diversity, are more likely to have biased and discriminating views.
-Additionally, it is possible that violent displays of masculinity and intolerance will continue to exist as a consequence of education that either promotes traditional gender standards or minimizes the relevance of critical media literacy.
-
-##Implications
-
-On the implication of the findings, it is evident that programs to eliminate support for hate crimes should include both individual attitude change and the broader context, given that the focus is on demographics and society.
-This covers those promotion of public health that is gender-based and specializes in changing the cultural modeling around masculinity [@Courtenay2000], as well as those reconstructors of social policies envisaging the reduction of economic and social inequalities that can amplify the competition of mates [@Wilkinson2009].
-\newpage
-
 # References

### 2024-02-15 replications/scripts/fig1_replication.R
Adjust the proportion of the chart in the pdf file

@@ -5,11 +5,10 @@
 # Contact: xiyou.wang@mail.utoronto
 # License: MIT
 
-# Load libraries
 library(ggplot2)
 
 # Load and clean data for wave 4
-d <- readRDS("inputs/data/fig1data")
+d <- readRDS(here::here("inputs/data/fig1data"))
 d <- lapply(d, function(x) round(x, 2))
 
 # Classify all p-value
@@ -20,7 +19,7 @@ p_values_total <- d[[3]][c(3, 6, 9)]
 # Summary of basic data information
 summary_data <- data.frame(
   group = rep(c("All", "Male (18-44)", "Male (30-40)"), each = 3),
-  tercile = rep(c("1st tercile", "2nd tercile", "3rd tercile"), 3),
+  tercile = rep(c("1st\ntercile", "2nd\ntercile", "3rd\ntercile"), 3),
   mean = d[[1]],
   se = d[[2]]
 )
@@ -28,12 +27,12 @@ summary_data <- data.frame(
 # Function to add p-value annotations
 add_pvalues <- function(plot, p_values_1st_2nd, p_values_2nd_3rd, p_values_total) {
   plot <- plot + geom_text(data = subset(summary_data, tercile == "2nd tercile" & group == unique(summary_data$group)[1]), 
-                           aes(label = sprintf("pv = %.2f", p_values_1st_2nd[1]), y = 0.4),
-                           hjust = 1.4, vjust = 30)
+                           aes(label = sprintf("pv = %.2f", p_values_1st_2nd[1]), y = 0.2),
+                           size = 2.7)
   
   plot <- plot + geom_text(data = subset(summary_data, tercile == "3rd tercile" & group == unique(summary_data$group)[1]), 
                            aes(label = sprintf("pv = %.2f", p_values_2nd_3rd[1]), y = 0.4),
-                           hjust = 1.4, vjust = 30)
+                           hjust = 1.15, vjust = 20, size = 2.7)
   
   plot <- plot + geom_text(data = subset(summary_data, tercile == "2nd tercile" & group == unique(summary_data$group)[1]), 
                            aes(label = sprintf("pv = %.2f", p_values_total[1]), y = 0.4), 
@@ -41,11 +40,11 @@ add_pvalues <- function(plot, p_values_1st_2nd, p_values_2nd_3rd, p_values_total
   
   plot <- plot + geom_text(data = subset(summary_data, tercile == "2nd tercile" & group == unique(summary_data$group)[2]), 
[…]

### 2024-02-15 outputs/paper.Rmd
final update with complete paper

@@
 output:
-  bookdown::pdf_document2
-toc: TRUE
+  bookdown::pdf_document2:
+    toc-title: "Contents"
+toc: true
+toc-title: "Contents"
+number-sections: true
+format: pdf
 bibliography: references.bib
@@
 ```
-
 \newpage
-
 # Introduction
 
-Hate crime and gender imbalance have emerged as a pressing issue in today's society, sparking fears over the disruption of stable relationship formation and social cohesion (FBI 5; Sage books) Explained as the criminal act motivated by bias or prejudice towards particular groups such as race, religion, gender, or identity-based characteristics, hate crimes pose a crucial threat to individuals' and communities' safety.
+Hate crime and gender imbalance have emerged as a pressing issue in today's society, sparking fears over the disruption of stable relationship formation and social cohesion [@chakraborti2015hate] explained as the criminal act motivated by bias or prejudice towards particular groups such as race, religion, gender, or identity-based characteristics, hate crimes pose a crucial threat to individuals' and communities' safety.
 Characterized by disparities in gender imbalance in the portion of men to women within a population has garnered attention for social dynamics and interpersonal relationships due to potential implications [@shang2022tackling].
@@
 
-Drawing data from different sources, we seek to elucidate complex phenomena between interconnections and their broader societal implications (FBI 5; Sage books).
+Drawing data from different sources, we seek to elucidate complex phenomena between interconnections and their broader societal implications [@chakraborti2015hate].
 Through empirical and theoretical analysis rigorously, contribute to a better understanding of these factors during hate-motivated behavior and gender imbalances informing evidence-based intervention and initiatives policies seeking to foster more excellent inclusive gender balance and tolerance in society [@chakraborti2015hate].
@@
 
-#Data
+\newpage
+# Data
 
@@
 
+\newpage
 # Results
 
-```{r fig1, echo=FALSE, warning=FALSE, message=FALSE, fig.cap="Excess Males at the Municipality Level and Individuals’ Perceived Mate Competition"}
+```{r fig-1, echo=FALSE, warning=FALSE, message=FALSE, fig.cap="Excess Males at the Municipality Level and Individuals’ Perceived Mate Competition"}
 # Load libraries
@@
   group = rep(c("All", "Male (18-44)", "Male (30-40)"), each = 3),
-  tercile = rep(c("1st tercile", "2nd tercile", "3rd tercile"), 3),
+  tercile = rep(c("1st\ntercile", "2nd\ntercile", "3rd\ntercile"), 3),
   mean = d[[1]],
@@
 add_pvalues <- function(plot, p_values_1st_2nd, p_values_2nd_3rd, p_values_total) {
-  plot <- plot + geom_text(data = subset(summary_data, tercile == "2nd tercile" & group == unique(summary_data$group)[1]), 
+  plot <- plot + geom_text(data = subset(summary_data, tercile == "2nd\ntercile" & group == unique(summary_data$group)[1]), 
                            aes(label = sprintf("pv = %.2f", p_values_1st_2nd[1]), y = 0.4),
-                           hjust = 1.15, vjust = 25, size = 2.7)
-
-  plot <- plot + geom_text(data = subset(summary_data, tercile == "3rd tercile" & group == unique(summary_data$group)[1]), 
-                           aes(label = sprintf("pv = %.2f", p_values_2nd_3rd[1]), y = 0.4),
                            hjust = 1.15, vjust = 20, size = 2.7)
 
-  plot <- plot + geom_text(data = subset(summary_data, tercile == "2nd tercile" & group == unique(summary_data$group)[1]), 
+  plot <- plot + geom_text(data = subset(summary_data, tercile == "3rd\ntercile" & group == unique(summary_data$group)[1]), 
+                           aes(label = sprintf("pv = %.2f", p_values_2nd_3rd[1]), y = 0.4),
+                           hjust = 1.15, vjust = 15, size = 2.7)
+
+  plot <- plot + geom_text(data = subset(summary_data, tercile == "2nd\ntercile" & group == unique(summary_data$group)[1]), 
                            aes(label = sprintf("pv = %.2f", p_values_total[1]), y = 0.4), 
@@
 
-  plot <- plot + geom_text(data = subset(summary_data, tercile == "2nd tercile" & group == unique(summary_data$group)[2]), 
+  plot <- plot + geom_text(data = subset(summary_data, tercile == "2nd\ntercile" & group == unique(summary_data$group)[2]), 
                            aes(label = sprintf("pv = %.2f", p_values_1st_2nd[2]), y = 0.5),
-                           hjust = 1.15, vjust = 25, size = 2.7)
-
-  plot <- plot + geom_text(data = subset(summary_data, tercile == "3rd tercile" & group == unique(summary_data$group)[2]), 
-                           aes(label = sprintf("pv = %.2f", p_values_2nd_3rd[2]), y = 0.5),
                            hjust = 1.15, vjust = 20, size = 2.7)
 
-  plot <- plot + geom_text(data = subset(summary_data, tercile == "2nd tercile" & group == unique(summary_data$group)[2]), 
+  plot <- plot + geom_text(data = subset(summary_data, tercile == "3rd\ntercile" & group == unique(summary_data$group)[2]), 
+                           aes(label = sprintf("pv = %.2f", p_values_2nd_3rd[2]), y = 0.5),
+                           hjust = 1.15, vjust = 15, size = 2.7)
+
+  plot <- plot + geom_text(data = subset(summary_data, tercile == "2nd\ntercile" & group == unique(summary_data$group)[2]), 
                            aes(label = sprintf("pv = %.2f", p_values_total[2]), y = 0.5), 
@@
 
-  plot <- plot + geom_text(data = subset(summary_data, tercile == "2nd tercile" & group == unique(summary_data$group)[3]), 
+  plot <- plot + geom_text(data = subset(summary_data, tercile == "2nd\ntercile" & group == unique(summary_data$group)[3]), 
                            aes(label = sprintf("pv = %.2f", p_values_1st_2nd[3]), y = 0.7),
-                           hjust = 1.15, vjust = 25, size = 2.7)
-
-  plot <- plot + geom_text(data = subset(summary_data, tercile == "3rd tercile" & group == unique(summary_data$group)[3]), 
-                           aes(label = sprintf("pv = %.2f", p_values_2nd_3rd[3]), y = 0.7),
                            hjust = 1.15, vjust = 20, size = 2.7)
 
-  plot <- plot + geom_text(data = subset(summary_data, tercile == "2nd tercile" & group == unique(summary_data$group)[3]), 
+  plot <- plot + geom_text(data = subset(summary_data, tercile == "3rd\ntercile" & group == unique(summary_data$group)[3]), 
+                           aes(label = sprintf("pv = %.2f", p_values_2nd_3rd[3]), y = 0.7),
+                           hjust = 1.15, vjust = 15, size = 2.7)
+
+  plot <- plot + geom_text(data = subset(summary_data, tercile == "2nd\ntercile" & group == unique(summary_data$group)[3]), 
                            aes(label = sprintf("pv = %.2f", p_values_total[3]), y = 0.7), 
@@
   theme(
-    strip.text = element_text(size = 20)
+    strip.text = element_text(size = 15)
   )
@@
 These p-values serve as a rigorous metric, emphasizing the reliability of the depicted correlations.
+\newpage
 
-```{r fig2, echo=FALSE, warning=FALSE, message=FALSE, fig.cap="Proportion of Respondents Who Agree with\nEach of the Four Hate Crime Statements"}
+```{r fig-2, echo=FALSE, warning=FALSE, message=FALSE, fig.cap="Proportion of Respondents Who Agree with\nEach of the Four Hate Crime Statements"}
 # Load data
@@
 This visual comparison shows differences in respondent agreement levels based on how the questions were asked, with direct questioning generally eliciting higher agreement levels.
+\newpage
 
-```{r fig3, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Estimated Effects of MateCompetition on Support for HateCrime"}
+```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Estimated Effects of MateCompetition on Support for HateCrime"}
+#| label: fig-3
 # Calculate points and standard errors again for clarity
@@
 
+\newpage
 # Discussion
 
-##Finding
+## Finding
 
-Figure \@ref(fig:fig1) illustrates a positive correlation between the number of excess males in a population and the perception of mate competition, especially among men aged 30-40.
+@fig-1 illustrates a positive correlation between the number of excess males in a population and the perception of mate competition, especially among men aged 30-40.
 This demographic trend imply that there is an increased sense of rivalry for potential mates in areas with more males.
 While the graph does not directly discuss hate crimes, the concept ties into broader social issues where such demographic imbalances may heighten competitive behaviors, potentially influencing social tensions and actions, including hate crimes.
-In Figure \@ref(fig:fig2), two types of responses are depicted for the statement "Only Means (List)"—one from the list experiment and one from direct questioning.
+In @fig-2, two types of responses are depicted for the statement "Only Means (List)", one from the list experiment and one from direct questioning.
 The bar representing the list experiment is indeed lower than that for the direct questioning for the statement "Only Means".
 This suggest that when individuals are provided with a method that offers anonymity and reduces the pressure to conform to social norms, they might be less likely to agree with statements supporting hate crime, contrary to what might be expected.
-When considering the impact of mate competition on attitudes towards hate crimes Figure \@ref(fig:fig3), it's crucial to consider the evolutionary psychology perspective, which suggests that competition for mates can increase intergroup hostility and aggression [@Buss1997].
+When considering the impact of mate competition on attitudes towards hate crimes @fig-3, it's crucial to consider the evolutionary psychology perspective, which suggests that competition for mates can increase intergroup hostility and aggression [@Buss1997].
 These behaviors may be exacerbated in environments with a skewed sex ratio, as individuals may perceive greater competition for potential partners, heightening in-group biases and out-group derogation [@Pedersen1991].
 
-##The Interplay of Demographics and Sociocultural Factors
+## The Interplay of Demographics and Sociocultural Factors
 
@@
 
-##Masculinity
+## Masculinity
 
@@
 
-##Digital media and educational inequality
+## Digital media and educational inequality
 
@@
 
-##Educational inequalities
+## Educational inequalities
 
@@
 
-##Implications
+## Implications
 
@@
 This covers those promotion of public health that is gender-based and specializes in changing the cultural modeling around masculinity [@Courtenay2000], as well as those reconstructors of social policies envisaging the reduction of economic and social inequalities that can amplify the competition of mates [@Wilkinson2009].
-\newpage
+
+## Weakness and future direction
+
+Upon reflection, our study into hate crimes and immigrant conflict, aimed at illuminating key issues, inadvertently focused too narrowly, potentially simplifying the complex nuances involved.
+We endeavored to highlight the pressures immigrants place on local demographics, a topic often neglected in existing literature, in an attempt to fill a significant knowledge gap.
+However, despite our detailed analysis and empirical data, our exploration may seem superficial upon closer examination.
+Recognizing this, we see the value in a more thorough examination of demographics likely to engage in mate competition, which does not always lead to hate crimes.Additionally, expanding our dataset to include women's experiences and situations in this context represents a promising direction for future research, suggesting a broader understanding of the underlying social tensions.
+This realization highlights the necessity of extending our analytical scope to include a variety of factors and perspectives, aiming for a more detailed understanding of the complex dynamics of migration, social stress, and hate crimes.
+Considering the limitations of our current study, our future efforts will concentrate on significantly expanding and diversifying our analysis framework.
+For example, improving gender representation involves incorporating data that reflect women's unique perspectives and experiences, thereby adding depth and breadth to our analyses.
+Furthermore, the prospect of collaborating with interdisciplinary teams from fields such as psychology and sociology offers the potential to collect a more comprehensive dataset, which is crucial for developing more effective strategies to mitigate hate crimes and immigration conflicts.
+By integrating insights from various disciplines, we aim to formulate well-informed and inclusive policy proposals that foster social cohesion and address the root causes of intergroup conflicts.
 

### 2024-02-15 outputs/paper.qmd
final update with complete paper

--- 2024-02-15 outputs/paper.Rmd
@@
                            aes(label = sprintf("pv = %.2f", p_values_total[1]), y = 0.4), 
-                           vjust = 0, fontface = "italic", size = 5)
+                           vjust = 2, fontface = "italic", size = 5)
 
@@
                            aes(label = sprintf("pv = %.2f", p_values_total[2]), y = 0.5), 
-                           vjust = 0, fontface = "italic", size = 5)
+                           vjust = 2, fontface = "italic", size = 5)
 
@@
                            aes(label = sprintf("pv = %.2f", p_values_total[3]), y = 0.7), 
-                           vjust = 0, fontface = "italic", size = 5)
+                           vjust = 2, fontface = "italic", size = 5)
 
@@
 bar_name <- rep("", 5)
-bar_name_u <- c("Only Means\n(List)", "Only Means\n(Direct)", "Justified", "Message", "Condemn")
+bar_name_u <- c("Only Means\n(List)", "Only Means", "Justified", "Message", "Condemn")
 
 # Set plot format
-par(mfrow = c(2, 2), mar = c(5, 5, 4, 2))
+par(mfrow = c(2, 2), mar = c(4, 4, 1, 2))
 
@@
 
+\newpage
 # References

### 2024-02-15 outputs/paper.Rmd
final

--- 2024-02-14 outputs/paper.Rmd
@@
----
-title: "Explaining Hate Crime and Immigrant Conflict: A New Perspective Study of Mate Competition"
-subtitle: "Reproduction of 'Hate Crimes and Gender Imbalances: Fears over MateCompetition and Violence against Refugees'(Dancygier, Egami, Jamal & Rischke, 2022)"
-author: Guoguo Lv, Xiyou Wang, Yetao Guo
-thanks: "Code and data are available at: https://github.com/wxywxy666/Hate-Crimes-and-Gender-Imbalances.
-A replication of various aspects in this paper are available at: https://onlinelibrary.wiley.com/doi/epdf/10.1111/ajps.12595"
-date: "`r format(Sys.time(), '%d %B %Y')`"
-abstract: "The study examines the correlation between gender imbalance, specifically the excess of males in a population, and the consequent competition for mates, as well as the attitudes towards hate crimes against refugees.
-Utilizing data from various sources, it aims to illuminate the complex interplay between mate competition and the endorsement of hate crimes, addressing gaps in current research.
-The findings suggest that higher male ratios may contribute to increased mate competition and potentially to greater support for hate-motivated acts against refugees.
-This research underscores the need for policies that promote gender balance and societal tolerance, contributing to the prevention of hate crimes and enhancing social cohesion."
-output:
-  bookdown::pdf_document2
-toc: TRUE
-bibliography: references.bib
----
+git config --global user.name "wxywxy666"
+git config --global user.email "wxy1700774887@outlook.com"
+git config --global --list
 
-```{r setup, include=FALSE}
-# Load libraries
-library(ggplot2)
-library(here)
-```
-\newpage
-# Introduction
+gitcreds_set()
+create_github_token()
 
-<!-- Background / Broader Context -->
-
-Hate crime and gender imbalance have emerged as a pressing issue in today's society, sparking fears over the disruption of stable relationship formation and social cohesion (FBI 5; Sage books) Explained as the criminal act motivated by bias or prejudice towards particular groups such as race, religion, gender, or identity-based characteristics, hate crimes pose a crucial threat to individuals' and communities' safety.
-Characterized by disparities in gender imbalance in the portion of men to women within a population has garnered attention for social dynamics and interpersonal relationships due to potential implications (shang2022tackling).
-
-The link between hate crime and gender imbalance, with factors interrelated influencing both phenomena, is multifaceted and complex (chakraborti2015hate).
-Certain groups, especially women and members of marginalized communities, often experience gender-based inequalities and are affected disproportionately by discrimination and acts of violence.
-Further, whether in the form of skewed sex ratios or imbalance in social opportunities and economic gender imbalances, it can lead to frustrations and resentment feelings among individuals, potentially increasing animosity toward specific groups and increasing hate-motivated likelihood (leote2023female).
-
-Although increased recognition of hate crime and gender imbalance intertwined nature, comprehensive analysis by assessing their intersection remains limited(james2021federal).
-The current has focused on the aspects isolated from their phenomena, overlooking the intricate interplay between them.
-Therefore, there is a significant need for studies that explore the relationship between gender imbalance and hate crimes, thus focusing on the mechanism underlying individual well-being and social cohesion implications.
-
-This study aims to cross the gap by investigating and addressing the following questions:
-
--   what is the relationship between the proportion of excess males in a municipality and the perceived competition for mates among the population?
--   what are the attitudes towards hate crimes against refugees?
--   what is the relationship between mate competition and support for hate crimes against refugees?
-
-Drawing data from different sources, we seek to elucidate complex phenomena between interconnections and their broader societal implications (FBI 5; Sage books).
-Through empirical and theoretical analysis rigorously, contribute to a better understanding of these factors during hate-motivated behavior and gender imbalances informing evidence-based intervention and initiatives policies seeking to foster more excellent inclusive gender balance and tolerance in society (chakraborti2015hate).
-
-# Data
-
-## Data Source and Methodology
-
-## Attributes
-
-# Results
-
-```{r fig1, echo=FALSE, warning=FALSE, message=FALSE, fig.cap="Excess Malesat the Municipality Level and Individuals’Perceived Mate Competition"}
-# Load libraries
-library(ggplot2)
-
-# Load and clean data for wave 4
-d <- readRDS(here::here("inputs/data/fig1data"))
-d <- lapply(d, function(x) round(x, 2))
-
-# Classify all p-value
-p_values_1st_2nd <- d[[3]][c(1, 4, 7)]
-p_values_2nd_3rd <- d[[3]][c(2, 5,8 )]
-p_values_total <- d[[3]][c(3, 6, 9)]
-
-# Summary of basic data information
-summary_data <- data.frame(
-  group = rep(c("All", "Male (18-44)", "Male (30-40)"), each = 3),
-  tercile = rep(c("1st tercile", "2nd tercile", "3rd tercile"), 3),
-  mean = d[[1]],
-  se = d[[2]]
-)
-
-# Function to add p-value annotations
-add_pvalues <- function(plot, p_values_1st_2nd, p_values_2nd_3rd, p_values_total) {
-  plot <- plot + geom_text(data = subset(summary_data, tercile == "2nd tercile" & group == unique(summary_data$group)[1]), 
-                           aes(label = sprintf("pv = %.2f", p_values_1st_2nd[1]), y = 0.4),
-                           hjust = 1.4, vjust = 30)
-
-  plot <- plot + geom_text(data = subset(summary_data, tercile == "3rd tercile" & group == unique(summary_data$group)[1]), 
-                           aes(label = sprintf("pv = %.2f", p_values_2nd_3rd[1]), y = 0.4),
-                           hjust = 1.4, vjust = 30)
-
-  plot <- plot + geom_text(data = subset(summary_data, tercile == "2nd tercile" & group == unique(summary_data$group)[1]), 
-                           aes(label = sprintf("pv = %.2f", p_values_total[1]), y = 0.4), 
-                           vjust = 0, fontface = "italic", size = 5)
-
-  plot <- plot + geom_text(data = subset(summary_data, tercile == "2nd tercile" & group == unique(summary_data$group)[2]), 
-                           aes(label = sprintf("pv = %.2f", p_values_1st_2nd[2]), y = 0.5),
-                           hjust = 1.4, vjust = 30)
-
-  plot <- plot + geom_text(data = subset(summary_data, tercile == "3rd tercile" & group == unique(summary_data$group)[2]), 
-                           aes(label = sprintf("pv = %.2f", p_values_2nd_3rd[2]), y = 0.5),
-                           hjust = 1.4, vjust = 30)
-
-  plot <- plot + geom_text(data = subset(summary_data, tercile == "2nd tercile" & group == unique(summary_data$group)[2]), 
-                           aes(label = sprintf("pv = %.2f", p_values_total[2]), y = 0.5), 
-                           vjust = 0, fontface = "italic", size = 5)
-
-  plot <- plot + geom_text(data = subset(summary_data, tercile == "2nd tercile" & group == unique(summary_data$group)[3]), 
-                           aes(label = sprintf("pv = %.2f", p_values_1st_2nd[3]), y = 0.7),
-                           hjust = 1.4, vjust = 30)
-
-  plot <- plot + geom_text(data = subset(summary_data, tercile == "3rd tercile" & group == unique(summary_data$group)[3]), 
-                           aes(label = sprintf("pv = %.2f", p_values_2nd_3rd[3]), y = 0.7),
-                           hjust = 1.4, vjust = 30)
-
-  plot <- plot + geom_text(data = subset(summary_data, tercile == "2nd tercile" & group == unique(summary_data$group)[3]), 
-                           aes(label = sprintf("pv = %.2f", p_values_total[3]), y = 0.7), 
-                           vjust = 0, fontface = "italic", size = 5)
-
-  return(plot)
-}
-
-# Initial plot
-p <- ggplot(summary_data, aes(x = tercile, y = mean, group = group)) +
-  geom_errorbar(aes(ymin = mean - se, ymax = mean + se), width = 0.2) +
-  geom_point() +
-  facet_wrap(~group, scales = "free_y") +
-  theme_minimal() +
-  labs(
-    x = "Excess Males",
-    y = "Proportion Receiving Male Competition",
-    group = "Group Name"
-  ) +
-  theme(
-    strip.text = element_text(size = 20)
-  )
-
-# Use function to add p-value annotation
-add_pvalues(p, p_values_1st_2nd, p_values_2nd_3rd, p_values_total)
-```
-
-The chart effectively shows the correlation between the surplus of males in a population and the resultant perceptions of mate competition, which has been divided into three separate cohorts.
-The first cohort comprises the general population, offering a broad perspective on the trend, then more closely in two specific age groups of males: 18-44 and 30-40.
-The data from the chart is organized into terciles, which echoes the changing male surplus levels.
-Using this approach facilitates a better analysis, as it portrays a consistent pattern where the idea of mate competition escalates in relation to the increase in male surplus.
-It is noteworthy to note that this pattern is most marked within the 30-40 age demographic.
-Interpreting this information shows a raised sensitivity to demographic shifts within this group.
-The chart utilizes a clear visual methodology to show these insights.
-The dots represent each perception of the tercile.
-The dots have also been positioned strategically to convey the central tendency of the data.
-P-values with meticulous annotation surround these dots, providing a statistical testament to the importance of the observed trends.
-These p-values serve as a rigorous metric, emphasizing the reliability of the depicted correlations.
-
-```{r demgraphs, echo=FALSE, warning=FALSE, message=FALSE, fig.cap="Proportion of Respondents Who Agree with\nEach of the Four Hate Crime Statements"}
-# Load data
-points_list <- readRDS(here::here("inputs/data/points"))
-se_p_list <- readRDS(here::here("inputs/data/se"))
-
-# Bar names
-bar_name <- rep("", 5)
-bar_name_u <- c("Only Means\n(List)", "Only Means\n(Direct)", "Justified", "Message", "Condemn")
-
-# Set plot format
-par(mfrow = c(2, 2), mar = c(5, 5, 4, 2))
-
-# Loop to make 4 panels
-for (i in 1:4) {
-  point <- points_list[[i]]
-  se_p <- se_p_list[[i]]
-
-  base <- barplot(point, ylim = c(0, 0.3), names.arg = bar_name, 
-                  col = c("cornflowerblue", rep("lightblue1", 4)),
-                  ylab = "Proportion of respondents",
-                  las = 2,
-                  main = paste("Wave", i))
-
-  arrows(base, point - 1.96*se_p, base, point + 1.96*se_p, 
-         lwd = 2, angle = 90, length = 0.05, code = 3,
-         col = adjustcolor("black", alpha.f = 0.7))
-
-  mtext(bar_name_u, at = base, side = 1, line = 2.5, cex = 1)
-}
-```
-
-This bar chart contains four panels that present the results of the survey on respondents' level of agreement with four different hate crime statements collected in a total of four waves of the survey study.
-Under the "Estimate from List Experiment," there is only one category titled "Only Means (List)" with a single dark blue bar.
-This bar represents the proportion of respondents who agreed with a statement when asked indirectly, as part of a list experiment.
-The proportion is around 0.15.
-The "Direct Questions" section includes three light blue bars for the categories.
-Each category represents a different hate crime statement where respondents were asked directly.
-"Only Means (Direct)" has a proportion slightly above 0.15, similar to the indirect estimate but with direct questioning.
-"Justified" shows a slightly lower proportion of agreement, just below the 0.15 mark.
-"Message" has a proportion just above 0.15, indicating a similar level of agreement to the "Only Means (Direct)" statement.
-"Condemn" displays the highest agreement, with a proportion close to 0.25, suggesting that more respondents agree with a statement that presumably condemns hate crimes.
-This visual comparison shows differences in respondent agreement levels based on how the questions were asked, with direct questioning generally eliciting higher agreement levels.
-
-```{r cohorttab, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Estimated Effects of MateCompetition on Support for HateCrime"}
-# Calculate points and standard errors again for clarity
-point <- readRDS(here::here("inputs/data/points"))[[5]]
-se <- readRDS(here::here("inputs/data/se"))[[5]]
-
-# Preparation of figure settings
-colors <- c("skyblue", "salmon", "lightgreen", "gold", "violet")
-pch_values <- c(15, 16, 17, 18, 19)
-names_point <- c("Only Means", "Justified", "Message", "Prevent", "Condemn")
-
-par(mar = c(5, 5, 4, 2))
-
-# Initial plot
-plot(seq(1:5), point, pch = pch_values, col = colors, ylim = c(-0.05, 0.35), xlim = c(0.5, 5.5), 
-     xlab = "", xaxt = "n", ylab = "Estimated Effects", 
-     cex.lab = 1.25, cex.axis = 1.25, cex.main = 1.5, cex = 1.5)
-
-segments(seq(1:5), point - 1.96*se, 
-         seq(1:5), point + 1.96*se, col = colors, lwd = 2)
-
-Axis(side = 1, at = seq(1:5), labels = names_point, cex.axis = 1.25)
-
-abline(h = 0, lty = 2)
-
-text(2.5, 0.30, "Significant Effects", cex = 0.8)
-
-# Add four arrows
-for (i in 1:4) {
-  arrows(2.5, 0.29, i, point[i] + 0.02, length = 0.05)
-}
-```
-This graph depicts the relationship between mate competition and the level of support for hate crime through five distinct categories.
-Each category is represented by a point on the graph, with a vertical line that indicates the confidence interval or error range around the estimate.
-The "Only Means" category has a low estimated effect size around 0.15 with a relatively small confidence interval.
-The "Justified" category shows a slightly higher effect size than "Only Means", also with a small confidence interval.
-The "Message" category has an estimated effect similar to "Justified".
-The "Prevent" category shows the highest estimated effect size than the previous ones, around 0.2.
-Finally, the "Condemn" category has an effect size close to zero, with a confidence interval that crosses the zero line.
-The graph is marked with a horizontal dashed line at the zero mark, which is likely indicating the point of no effect.
-The Significant Effects are marked on the graph above the first four categories, suggesting that these categories' effect size is statistically significant, whereas the remaining category is not explicitly marked as significant.
-
-# Discussion
-
-The relationship between demographic variables and social attitudes, as depicted in the provided figures, is a complex interplay influenced by many factors. 
-When considering the impact of mate competition on attitudes towards hate crimes (Figure 4), it's crucial to consider the evolutionary psychology perspective, which suggests that competition for mates can increase intergroup hostility and aggression (Buss & Shackelford, 1997).
-These behaviors may be exacerbated in environments with a skewed sex ratio, as individuals may perceive greater competition for potential partners, heightening in-group biases and out-group derogation (Pedersen, 1991).
-In Figure 3, there are two types of responses depicted for the statement "Only Means (List)"—one from the list experiment and one from direct questioning.
-The bar representing the list experiment is indeed lower than that for the direct questioning for the statement "Only Means".
-This could suggest that when individuals are provided with a method that offers anonymity and reduces the pressure to conform to social norms, they might be less likely to agree with statements supporting hate crime, contrary to what might be expected.
-Figure 2 illustrates a positive correlation between the number of excess males in a population and the perception of mate competition, especially among men aged 30-40.
-This demographic trend could imply that in areas with more males, there is an increased sense of rivalry for potential mates.
-While the graph does not directly discuss hate crimes, the concept ties into broader social issues where such demographic imbalances may heighten competitive behaviors, potentially influencing social tensions and actions, including hate crimes.
-To better understand these dynamics, we can look at the intersection of demographic pressures and socio-cultural factors that shape attitudes towards hate crimes.
-Cultural narratives that equate masculinity with dominance and control may influence these attitudes (Connell, 2005).
-In societies where masculinity is closely linked with sexual conquest and competition(Baumeister & Vohs, 2004), excess males may experience heightened psychological stress, potentially contributing to aggressive and hostile behaviors towards out-groups.
-Considering the implications of these findings, it is clear that interventions to reduce support for hate crimes must address not only individual attitudes but also the broader demographic and socio-cultural context.
-This may include public health approaches that focus on changing cultural narratives around masculinity (Courtenay, 2000), as well as social policies aimed at reducing economic and social inequalities that can exacerbate mate competition (Wilkinson & Pickett, 2009).
-
-\newpage
-
-# References
+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

### 2024-02-15 outputs/paper.qmd
update Rmd format paper
final

@@
 subtitle: "Reproduction of 'Hate Crimes and Gender Imbalances: Fears over MateCompetition and Violence against Refugees'(Dancygier, Egami, Jamal & Rischke, 2022)"
-author: Guoguo Lv, Xiyou Wang, Yetao Guo
+author: Guoguo Lyu, Xiyou Wang, Yetao Guo
 thanks: "Code and data are available at: https://github.com/wxywxy666/Hate-Crimes-and-Gender-Imbalances.
@@
 
-While the original paper used Stata [@Stata] for data processing and analysis in its replication package, we use R [@R] for all data wrangling and analysis and R packages list [@list] to clean the original data, ggplot2 [@ggplot2] to produce the figures and readstata13 [@readstata13] to read the dta files.
+While the original paper used Stata [@Stata] for data processing and analysis in its replication package, we use R [@R] for all data wrangling and analysis and R packages list [@list] to clean the original data, ggplot2 [@ggplot2] to produce the figures and readstata13 [@readstata13] to read the .dta files.
 
@@
 
-## The Interplay of Demographics and Sociocultural Factors
-
-In order to get a better idea of these relationships, what can be examined is the influences of demographic factors and social-cultural attitudes which trigger hate crimes.
-
 ## Masculinity
@@
 Therefore, an increase in the number of hate crimes is a possible outcome.
+
+In order to get a better idea of these relationships, what can be examined is the influences of demographic factors and social-cultural attitudes which trigger hate crimes.
 

### 2024-02-15 replications/scripts/00-simulate_data.R

@@ -1,0 +1,162 @@
+#### Preamble ####
+# Purpose: simulate data
+# Author: Xiyou Wang
+# Date: 12 February 2024
+# Contact: xiyou.wang@mail.utoronto
+# License: MIT
+
+# Set seed
+set.seed(888)
+
+# Genertate se_p_list
+se_p_list <- lapply(1:4, function(x) runif(5, 0.006, 0.009))
+se_p_list[[5]] <- runif(5, 0.018, 0.021)
+se_p_list[[6]] <- se_p_list[[5]]
+
+# Genertate points_list
+points_list <- lapply(1:4, function(x) runif(5, 0.15, 0.25))
+points_list[[5]] <- runif(5, 0.02, 0.20)
+points_list[[6]] <- points_list[[5]]
+
+# Genertate p-values
+pv <- list(
+  runif(9, min = 0.17, max = 0.47), # 第一组数据，范围从0.17到0.47，共9个值
+  runif(9, min = 0.01, max = 0.07), # 第二组数据，范围从0.01到0.07，共9个值
+  runif(9, min = 0.00, max = 0.40)  # 第三组数据，范围从0.00到0.40，共9个值
+)
+
+## #################
+## Figure 1
+## #################
+p_values_1st_2nd <- pv[[3]][c(1, 4, 7)]
+p_values_2nd_3rd <- pv[[3]][c(2, 5,8 )]
+p_values_total <- pv[[3]][c(3, 6, 9)]
+
+# Summary of basic data information
+summary_data <- data.frame(
+  group = rep(c("All", "Male (18-44)", "Male (30-40)"), each = 3),
+  tercile = rep(c("1st\ntercile", "2nd\ntercile", "3rd\ntercile"), 3),
+  mean = pv[[1]],
+  se = pv[[2]]
+)
+
+# Function to add p-value annotations
+add_pvalues <- function(plot, p_values_1st_2nd, p_values_2nd_3rd, p_values_total) {
+  plot <- plot + geom_text(data = subset(summary_data, tercile == "2nd tercile" & group == unique(summary_data$group)[1]), 
+                           aes(label = sprintf("pv = %.2f", p_values_1st_2nd[1]), y = 0.2),
+                           size = 2.7)
+  
+  plot <- plot + geom_text(data = subset(summary_data, tercile == "3rd tercile" & group == unique(summary_data$group)[1]), 
[…]

### 2024-02-15 replications/scripts/03-test_data.R

@@ -1,0 +1,23 @@
+# Load se_p_list and points_list
+se_p_list <- readRDS("inputs/data/se")
+se_p_list <- lapply(se_p_list, function(x) ifelse(is.na(x), 0, x))
+
+points_list <- readRDS("inputs/data/points")
+points_list <- lapply(points_list, function(x) ifelse(is.na(x), 0, x))
+# Load fig1 data
+pv <- readRDS("inputs/data/fig1data")
+
+# Test length
+if(length(se_p_list) == 6 && length(points_list) == 6 && length(pv) == 3) {
+  cat("List lengths are correct.\n")
+} else {
+  cat("Error in list lengths.\n")
+}
+
+# Test range
+if(check_data_range(se_p_list, 0, 0.05) && check_data_range(points_list, 0, 0.3) && check_data_range(pv[[3]], 0, 0.4)) {
+  cat("Data ranges in se_p_list, points_list and pv are correct.\n")
+} else {
+  cat("Error in data ranges of se_p_list or points_list or pv.\n")
+}
+
